---
title: "B_merge"
---

# LEALCO-BEH2: analyse data *from test task*

# Information

### Goal

### Inputs

The output file is a large .csv table containing the entire data of the file in a long format. It puts together the PsychoPy input files, the demographics, the VOT files as well as the relevant information from the debriefing questionnaire.

### Output

# Load packages

```{r}
library(dplyr)
library(tidyverse)
library(lme4)
library(buildmer)
library(emmeans)
library(lmerTest)
library(gridExtra)
source('R/utils.R')
```

# Set some custom settings

```{r}

#theme_set(theme_gray())
theme_set(theme_bw())
#pal1 = c("#2d8fd5", "#87cdff")
pal3 = c("#F5793A", "#4f5dab", "#858585")
pal1 = c("#66A054", "#D4aa00", "#858585")
pal2 = c("#138471", "#70beb1")
```

# Read files

Read files:

-   data: file containing the main data

-   norms: file (derived from the data file) containing naming norms based on untrained trials only

```{r}
# ================ read files
data <- read.csv('data/LEALCO-BEH2_test_merged_data.csv')
norms <- read.csv('data/LEALCO-BEH2_test_merged_naming_norms.csv')
demo <- read.csv('data/demographic/LEALCO-BEH2_demographics_data_test470046_2025-07-15_15-29.csv',  sep = ";", fileEncoding = "Latin1", check.names = F)
```

Make certain variables into factors

```{r}

# change name for some variable levels
demo$gender[demo$gender == 1] <- 'male' 
demo$gender[demo$gender == 2] <- 'female' 
demo$gender[demo$gender == 4] <- 'other' 
demo$gender[demo$gender == 5] <- 'no_answer' 

# make factors
data$subjID <- as_factor(data$subjID)
data$partner_order <- as_factor(data$partner_order)
data$block <- as_factor(data$block)
data$partner <- as_factor(data$partner)
data$class <- as_factor(data$class)
data$type <- as_factor(data$type)
data$test_partner <- as_factor(data$test_partner)
data$target_stimID <- as_factor(data$target_stimID)
data$correct <- as_factor(data$correct)
data$error <- as_factor(data$error)
data$target_label <- as_factor(data$target_label)
data$alternative_label <- as_factor(data$alternative_label)
data$produced_label <- as_factor(data$produced_label)

# relevel
levels(data$correct) <- c("other", "matching",  "non-matching")
data$correct <- relevel(data$correct,  'non-matching')
data$correct <- relevel(data$correct,  'matching')

# relevel
data$produced_label <- relevel(data$produced_label,  'label_B')
data$produced_label <- relevel(data$produced_label,  'label_A')

# create some new variables for primacy and recency
data <- data %>% 
  mutate(primacy = case_when(partner_order == 'A - B / A - B' ~ "A",
                       partner_order == 'A - B / B - A' ~ "A",
                       partner_order == 'B - A / B - A' ~ "B",
                       partner_order == 'B - A / A - B' ~ "B"))
data$primacy <- as_factor(data$primacy)

data <- data %>% 
  mutate(recency = case_when(partner_order == 'A - B / A - B' ~ "B",
                       partner_order == 'A - B / B - A' ~ "B",
                       partner_order == 'B - A / B - A' ~ "A",
                       partner_order == 'B - A / A - B' ~ "A"))
data$recency <- as_factor(data$recency)

data <- data %>%
  mutate(training_order = case_when(partner_order == 'A - B / A - B' ~ "AB",
                       partner_order == 'A - B / B - A' ~ "AB",
                       partner_order == 'B - A / B - A' ~ "BA",
                       partner_order == 'B - A / A - B' ~ "BA"))
data$training_order <- as_factor(data$training_order)

# add naming norms for the label that was actually produced by the subject
data <- data %>%
  mutate(exact_produced_label = case_when(produced_label == 'label_A' &  test_partner == 'A' ~ target_label,
                                          produced_label == 'label_A' &  test_partner == 'B' ~ alternative_label,
                                          produced_label == 'label_B' &  test_partner == 'B' ~ target_label,
                                          produced_label == 'label_B' &  test_partner == 'A' ~ alternative_label,
                                          produced_label == 'other' ~ 'other'))
data <- left_join(
  data,
  norms[norms$name != 'other',],
  by = c('exact_produced_label'))

```

For each trial, create new variable containing the perceived quality of teamwork, depending on the current partner (this just takes the correct value from the debriefing questionnaire, depending on which partner the trial took place with)

```{r}
# 
data$team  <- ifelse(data$partner == 'A', data$T101, data$T201)
```

# Preliminary data sanity checks

## (1) Check general error pattern

Here, the general error distribution (regardless of experimental condition) is assessed by subject. This can potentially constitute the basis for data exclusion.

| Code    | Meaning                                     |
|---------|---------------------------------------------|
| correct | said exactly what they were expected to say |
| 1       | compounded                                  |
| 2       | semantically related                        |
| 3       | phonologically related                      |
| 4       | unrelated                                   |
| 5       | misarticulation                             |
| 6       | other                                       |
| 7       | visual                                      |
| 8       | audio recording error                       |
| 9       | no response                                 |

: Table 1: Key for interpreting the "Error"" variable

```{r}
# plot accuracy counts by subject
pdf("output_figures/LEALCO-BEH2_raw screening.pdf")
p <- ggplot(data, aes(x=error, fill=error)) + 
  geom_bar() +
  facet_wrap(~subjID)
p
dev.off()
p

# count how many trials of each type
data %>% count(error) 

```

## (2) Check general RT pattern

Let's screen for anomalous RTs in the data files, which could have originated from inaccuracies in data reprocessing. It appears that no anomalies are (any longer) present in the data.

```{r}

# overall density plot
plot(density(data$VOT, na.rm = TRUE))

# zooming into the left part of the histogramm to spot anomalous VOTs (<400 ms), and export them.
hist(data$VOT, xlim=c(0, 1000), breaks = 1000)
dummy <- data[data$VOT < 400,]
write.csv(dummy, 'data/LEALCO-BEH2_test_anomalous_RTs.csv', row.names=FALSE, fileEncoding = "UTF-8")

# Look for NA values and export them.
dummy <- data[is.na(data$VOT),]
write.csv(dummy, 'data/LEALCO-BEH2_test_anomalousNA_RTs.csv', row.names=FALSE, fileEncoding = "UTF-8")

# histogramm fo ronly correct responses
hist(data$VOT[data$error == 'correct'], xlim=c(0, 1000), breaks = 1000)
plot(density(data$VOT[data$error == 'correct'], na.rm = TRUE))
```

## (3) Transform non-normal variables

After trying several normalization approaches, it appears that the **inverse** **normalization** is most appropriatel.

```{r}

# plot native VOTs
hist(data$VOT, breaks=500)

# plot log10 notmalized VOTs
data$VOTlog10 <- log10(data$VOT)
hist(data$VOTlog10, breaks=500)

# plot inverse normalized VOTs
data$VOTinv <- 1/data$VOT
hist(data$VOTinv, breaks=500)

# plot square root normalized VOTs
data$VOTsqrt <- sqrt(data$VOT)
hist(data$VOTsqrt, breaks=500)
```

## (4) Are there anomalous subjects?

Calculate descriptive across collapsed conditions. Note that no trials/subjects are excluded.

```{r}
data$is_correct <- 0
data$is_correct[data$error == 'correct'] <-1


# descritpives of accuracy: within-subjects
summary_acc_wSubj <- data %>%
  group_by(subjID) %>%
  summarise(mean_ACC = mean(is_correct), sd=sd(is_correct), sem=(sd(is_correct)/sqrt((length(is_correct)))))

# descritpives of accuracy: between-subjects
summary_acc_bSubj <- summary_acc_wSubj %>%
  summarise(grand_mean_ACC = mean(mean_ACC), sd=sd(mean_ACC), sem=(sd(mean_ACC)/sqrt((length(mean_ACC)))))

# descritpives of vot: within-subjects
summary_vot_wSubj <- data %>%
  filter(is_correct == 1) %>%
  group_by(subjID) %>%
  summarise(mean_VOT = mean(VOT), sd=sd(VOT), sem=(sd(VOT)/sqrt((length(VOT)))))

# descritpives of vot: between-subjects
summary_vot_bSubj <- summary_vot_wSubj %>%
  summarise(grand_mean_VOT = mean(mean_VOT), sd=sd(mean_VOT), sem=(sd(mean_VOT)/sqrt((length(mean_VOT)))))
```

# === 2-label items ===

## Subject exclusion

Select trained trials, with a focus on those that are valid, i.e. where no recording error occurred. We therefore exclude all trials coded as: (5) misarticulation, (6) other, (7) visual, (8) audio recording error (9) no response.

```{r}
data_2labels <- data %>%
  filter(type == '2-label') %>%
  filter(error %in% c('correct', 't1', 'a1', 't2', 'a2', 't3', 'a3', '4'))
```

Determine if any subjects need to be excluded based on data distribution for **accuracy** (collapsing all test conditions).

```{r}

# aggregate within subject
data_2labels_sum_wSubj <- data_2labels %>%
  group_by(subjID) %>%
  summarise(mean = mean(is_correct), sem=(sd(is_correct)/sqrt((length(is_correct)))), sd=sd(is_correct))

# aggregate between subjects
data_2labels_sum_bSubj <- data_2labels_sum_wSubj %>%
  summarise(grandMean = mean(mean), sem=(sd(mean)/sqrt((length(mean)))), sd=sd(mean))

# calculate SD intervals
plus2SD = data_2labels_sum_bSubj$grandMean + data_2labels_sum_bSubj$sd * 2
minus2SD = data_2labels_sum_bSubj$grandMean - data_2labels_sum_bSubj$sd * 2
plus25SD = data_2labels_sum_bSubj$grandMean + data_2labels_sum_bSubj$sd * 2.5
minus25SD = data_2labels_sum_bSubj$grandMean - data_2labels_sum_bSubj$sd * 2.5
plus3SD = data_2labels_sum_bSubj$grandMean + data_2labels_sum_bSubj$sd * 3
minus3SD = data_2labels_sum_bSubj$grandMean - data_2labels_sum_bSubj$sd * 3

# plot
pdf("output_figures/LEALCO-BEH2_acc_outliers.pdf")
ggplot(data_2labels_sum_wSubj, aes(x=mean)) +
  geom_dotplot() +
  geom_density(alpha=.2, fill="black") +
  geom_vline(aes(xintercept=data_2labels_sum_bSubj$grandMean)) +
  geom_vline(aes(xintercept=plus2SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus2SD), linetype="dashed") +
  geom_vline(aes(xintercept=plus25SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus25SD), linetype="dashed") +
  geom_vline(aes(xintercept=plus3SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus3SD), linetype="dashed") +
  annotate("text", x=plus2SD, y=3, label="+2SD", angle = 30) +
  annotate("text", x=minus2SD, y=3, label="-2SD", angle = 30) +
  annotate("text", x=plus25SD, y=3, label="+2.5SD", angle = 30) +
  annotate("text", x=minus25SD, y=3, label="-2.5SD", angle = 30) +
  annotate("text", x=plus3SD, y=3, label="+3SD", angle = 30) +
  annotate("text", x=minus3SD, y=3, label="-3SD", angle = 30) +
  annotate("text", x=data_2labels_sum_bSubj$grandMean, y=3, label="mean", angle = 30) +
  xlim(0,1) +
 ggtitle("Subject outliers based on accuracy")
dev.off()

# select outliers on the basis of +/-2SD
data_2labels_sum_wSubj[data_2labels_sum_wSubj$mean < minus25SD |
                       data_2labels_sum_wSubj$mean > plus25SD, ]
```

Do same thing with **naming latencies**.

```{r}

# aggregate within subject
data_2labels_sum_wSubj_vot <- data_2labels %>%
  group_by(subjID) %>%
  summarise(mean = mean(VOT), sem=(sd(VOT)/sqrt((length(VOT)))), sd=sd(VOT))

# aggregate between subjects
data_2labels_sum_bSubj_vot <- data_2labels_sum_wSubj_vot %>%
  summarise(grandMean = mean(mean), sem=(sd(mean)/sqrt((length(mean)))), sd=sd(mean))

# calculate SD intervals
plus2SD = data_2labels_sum_bSubj_vot$grandMean + data_2labels_sum_bSubj_vot$sd * 2
minus2SD = data_2labels_sum_bSubj_vot$grandMean - data_2labels_sum_bSubj_vot$sd * 2
plus25SD = data_2labels_sum_bSubj_vot$grandMean + data_2labels_sum_bSubj_vot$sd * 2.5
minus25SD = data_2labels_sum_bSubj_vot$grandMean - data_2labels_sum_bSubj_vot$sd * 2.5
plus3SD = data_2labels_sum_bSubj_vot$grandMean + data_2labels_sum_bSubj_vot$sd * 3
minus3SD = data_2labels_sum_bSubj_vot$grandMean - data_2labels_sum_bSubj_vot$sd * 3

# plot
pdf("output_figures/LEALCO-BEH2_vot_outliers.pdf")
ggplot(data_2labels_sum_wSubj_vot, aes(x=mean)) +
  geom_dotplot() +
  geom_density(alpha=.2, fill="black") +
  geom_vline(aes(xintercept=data_2labels_sum_bSubj_vot$grandMean)) +
  geom_vline(aes(xintercept=plus2SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus2SD), linetype="dashed") +
  geom_vline(aes(xintercept=plus25SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus25SD), linetype="dashed") +
  geom_vline(aes(xintercept=plus3SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus3SD), linetype="dashed") +
  annotate("text", x=plus2SD, y=3, label="+2SD", angle = 30) +
  annotate("text", x=minus2SD, y=3, label="-2SD", angle = 30) +
  annotate("text", x=plus25SD, y=3, label="+2.5SD", angle = 30) +
  annotate("text", x=minus25SD, y=3, label="-2.5SD", angle = 30) +
  annotate("text", x=plus3SD, y=3, label="+3SD", angle = 30) +
  annotate("text", x=minus3SD, y=3, label="-3SD", angle = 30) +
  annotate("text", x=data_2labels_sum_bSubj_vot$grandMean, y=3, label="mean", angle = 30) +
  xlim(0,NA) +
  ggtitle("Subject outliers based on naming latency (native)")
dev.off()

# select subjects with thada 
data_2labels_sum_wSubj_vot[data_2labels_sum_wSubj_vot$mean < minus25SD |
                       data_2labels_sum_wSubj_vot$mean > plus25SD, ]
```

Do the same with **inverted naming latencies**.

```{r}

# aggregate within subject
data_2labels_sum_wSubj_votINV <- data_2labels %>%
  group_by(subjID) %>%
  summarise(mean = mean(VOTinv), sem=(sd(VOTinv)/sqrt((length(VOTinv)))), sd=sd(VOTinv))

# aggregate between subjects
data_2labels_sum_bSubj_votINV <- data_2labels_sum_wSubj_votINV %>%
  summarise(grandMean = mean(mean), sem=(sd(mean)/sqrt((length(mean)))), sd=sd(mean))

# calculate SD intervals
plus2SD = data_2labels_sum_bSubj_votINV$grandMean + data_2labels_sum_bSubj_votINV$sd * 2
minus2SD = data_2labels_sum_bSubj_votINV$grandMean - data_2labels_sum_bSubj_votINV$sd * 2
plus25SD = data_2labels_sum_bSubj_votINV$grandMean + data_2labels_sum_bSubj_votINV$sd * 2.5
minus25SD = data_2labels_sum_bSubj_votINV$grandMean - data_2labels_sum_bSubj_votINV$sd * 2.5
plus3SD = data_2labels_sum_bSubj_votINV$grandMean + data_2labels_sum_bSubj_votINV$sd * 3
minus3SD = data_2labels_sum_bSubj_votINV$grandMean - data_2labels_sum_bSubj_votINV$sd * 3

# plot
pdf("output_figures/LEALCO-BEH2_votINV_outliers.pdf")
ggplot(data_2labels_sum_wSubj_votINV, aes(x=mean)) +
  geom_dotplot() +
  geom_density(alpha=.2, fill="black") +
  geom_vline(aes(xintercept=data_2labels_sum_bSubj_votINV$grandMean)) +
  geom_vline(aes(xintercept=plus2SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus2SD), linetype="dashed") +
  geom_vline(aes(xintercept=plus25SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus25SD), linetype="dashed") +
  geom_vline(aes(xintercept=plus3SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus3SD), linetype="dashed") +
  annotate("text", x=plus2SD, y=3, label="+2SD", angle = 30) +
  annotate("text", x=minus2SD, y=3, label="-2SD", angle = 30) +
  annotate("text", x=plus25SD, y=3, label="+2.5SD", angle = 30) +
  annotate("text", x=minus25SD, y=3, label="-2.5SD", angle = 30) +
  annotate("text", x=plus3SD, y=3, label="+3SD", angle = 30) +
  annotate("text", x=minus3SD, y=3, label="-3SD", angle = 30) +
  annotate("text", x=data_2labels_sum_bSubj_votINV$grandMean, y=3, label="mean", angle = 30) +
  ggtitle("Subject outliers based on naming latency (inverted)")
dev.off()

# select subjects with thada 
data_2labels_sum_wSubj_votINV[data_2labels_sum_wSubj_votINV$mean < minus25SD |
                       data_2labels_sum_wSubj_votINV$mean > plus25SD, ]
```

Overall, this condition-blind analysis of outliers showed that, for the **accuracy** measure, applying the following threshold results in excluding following subjects:

-   **2 SD:** 15, 25

-   **2.5 SD:** 15

-   **3 SD:** 15

For the **(native)** **VOT** measure applying the following threshold results in excluding following subjects:

-   **2 SD:** 15

-   **2.5 SD:** 15

-   **3 SD:** 15

For the **(inverted)** **VOT** measure applying the following threshold results in excluding following subjects:

-   **2 SD:** 15

-   **2.5 SD:** 15

-   **3 SD:** 15

Subjects 202, 225, 223 are excluded because they did not fulfimm the inclusion criteria or mistakes occurred suding stimulu spresentation.

We select the exclusion criteria of +/-2.5SD resulting in no exclusions..

```{r}
exclusion_acc <- c('202', '225', '223')
exclusion_vot <- c('202', '225', '223')
```

## Sample Stats

```{r}
# sample ACC
sample_ACC <- acc_wSubj_partner <- demo %>%
  filter(!subjID  %in%  exclusion_acc) %>%
  summarise(age_mean = mean(Alter), age_sd=sd(Alter),
            n=length(subjID))
sample_ACC_sex <- demo %>%
  filter(!subjID  %in%  exclusion_acc) %>%
  group_by(gender) %>%
  summarize(n= n()) %>%
  pivot_wider(names_from=gender, values_from=n)
sample_ACC <- cbind(sample_ACC, sample_ACC_sex)

# sample VOTinv
sample_VOTinv <- acc_wSubj_partner <- demo %>%
  filter(!subjID  %in%  exclusion_vot) %>%
  summarise(age_mean = mean(Alter), age_sd=sd(Alter),
            n=length(subjID))
sample_VOTinv_sex <- demo %>%
  filter(!subjID  %in%  exclusion_vot) %>%
  group_by(gender) %>%
  summarize(n= n()) %>%
  pivot_wider(names_from=gender, values_from=n)
sample_VOTinv <- cbind(sample_VOTinv, sample_VOTinv_sex)

# save
write.csv(sample_ACC, "output_stats/LEALCO-BEH2_demographic_summary_ACCsample.csv")
write.csv(sample_VOTinv, "output_stats/LEALCO-BEH2_demographic_summary_VOTinvsample.csv")
```

## Label Maintenance

### By Subject (congruency)

Here we just have a simple look at accuracy, that is we consider correct only those trials where the subject said *exactly* the word they were expected to say.

```{r}

# aggregate
acc_wSubj_congruency <- data_2labels %>%
  filter(!subjID %in%  exclusion_acc) %>%
  group_by(subjID, correct) %>%
  summarize(n=n()) %>%
  mutate(proportion = n / sum(n))

# save
write.csv(acc_wSubj_congruency, "output_stats/LEALCO-BEH2_accuracy_withinSubjects_congruency.csv", row.names = FALSE)

# plot (within subject)
pdf("output_figures/LEALCO-BEH2_accuracy_withinSubjects_congruency_barplot.pdf")
a <- ggplot(acc_wSubj_congruency, aes(y=proportion, x=correct, fill=correct)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal3) +
  labs(y="Produced labels (proportion)", x="Label Type") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylim(0,1) +
  facet_wrap(~subjID)
a
dev.off() 
a
```

```{r}
# aggregte (between subject)
acc_bSubj_congruency <- acc_wSubj_congruency %>%
  group_by(correct) %>%
  summarise(mean_bSubj = mean(proportion), sd_bSubj=sd(proportion), sem_bSubj=(sd(proportion)/sqrt((length(proportion)))), n_bSubj=length(proportion))

# save
write.csv(acc_bSubj_congruency, "output_stats/LEALCO-BEH2_accuracy_betweenSubjects_congruency.csv", row.names = FALSE)

# plot (within subject)
pdf("output_figures/LEALCO-BEH2_accuracy_betweenSubjects_congruency_barplot.pdf")
c <- ggplot(acc_bSubj_congruency, aes(y=mean_bSubj, x=correct, fill=correct)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  scale_fill_manual(values = pal3) +
   labs(y="Produced labels (proportion)", x="Label Type") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  theme(legend.title = element_blank()) +
  ylim(0,1)
c
dev.off()
c

# make other more transparent plot
pdf("output_figures/LEALCO-BEH2_accuracy_betweenSubjects_congruency_pointplot.pdf")
zz <- ggplot(acc_bSubj_congruency, aes(y=mean_bSubj, x=correct, fill=correct)) + 
  geom_point(data= acc_wSubj_congruency, aes(y=proportion, x=correct, color=correct), stat="identity", position=position_jitterdodge(jitter.width=0.3, dodge.width=.9), size=3) + 
  scale_colour_manual(values = pal3) +
    geom_point(stat="identity", color = "black", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Produced labels (proportion)", x="Label Type") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  theme(legend.title = element_blank()) +
  ylim(0,1)
zz
dev.off()
zz
```

### By Subject (Partner x Label)

```{r}
# aggregte (within subject)
acc_wSubj_partner <- data_2labels %>%
 filter(!subjID %in%  exclusion_acc) %>%
 group_by(subjID, partner, produced_label, .drop=FALSE) %>%
  summarize(n=n())

# calculate proportions 
counts <- data_2labels %>%
 filter(!subjID %in%  exclusion_acc) %>%
 group_by(subjID, partner,  .drop=FALSE) %>%
  summarize(n_total=n())
acc_wSubj_partner <- merge(x=acc_wSubj_partner,y=counts, 
             by=c("subjID", "partner"))
acc_wSubj_partner$proportion <- acc_wSubj_partner$n/acc_wSubj_partner$n_tot

# add correctness
acc_wSubj_partner$correct <- "other"
acc_wSubj_partner$correct[acc_wSubj_partner$partner == 'A' & acc_wSubj_partner$produced_label == 'label_A'] <- "matched"
acc_wSubj_partner$correct[acc_wSubj_partner$partner == 'B' & acc_wSubj_partner$produced_label == 'label_B'] <- "matched"
acc_wSubj_partner$correct[acc_wSubj_partner$partner == 'A' & acc_wSubj_partner$produced_label == 'label_A'] <- "matched"
acc_wSubj_partner$correct[acc_wSubj_partner$partner == 'B' & acc_wSubj_partner$produced_label == 'label_B'] <- "matched"
acc_wSubj_partner$correct[acc_wSubj_partner$partner == 'A' & acc_wSubj_partner$produced_label == 'label_B'] <- "non-matched"
acc_wSubj_partner$correct[acc_wSubj_partner$partner == 'B' & acc_wSubj_partner$produced_label == 'label_A'] <- "non-matched"

# plot
pdf("output_figures/LEALCO-BEH2_accuracy_withinSubjects_partner_barplot.pdf")
a <- ggplot(acc_wSubj_partner, aes(y=proportion, x=partner, group=produced_label, fill=produced_label)) +
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values =pal1) +
  labs(y="Precedent maintenance (proportion)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,1) +
  facet_wrap(~subjID)
a
dev.off()
a
```

```{r}
# aggregte (between subject)
acc_bSubj_partner <- acc_wSubj_partner %>%
  group_by(partner, produced_label, correct) %>%
  summarise(mean_bSubj = mean(proportion), sd_bSubj=sd(proportion), sem_bSubj=(sd(proportion)/sqrt((length(proportion)))), n_bSubj=length(proportion))

# save
write.csv(acc_bSubj_partner, "output_stats/LEALCO-BEH2_accuracy_betweenSubjects_partner.csv", row.names = FALSE)

# plot (within subject)
pdf("output_figures/LEALCO-BEH2_accuracy_betweenSubjects_partner_barplot.pdf")
c <- ggplot(acc_bSubj_partner, aes(y=mean_bSubj, x=partner, group=produced_label, fill=produced_label)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  scale_fill_manual(values = pal1) +
  labs(y="Precedent maintenance (proportion)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  theme(legend.title = element_blank()) +
  ylim(0,1) +
  geom_text(aes(label = produced_label), vjust = -2.5, position=position_dodge(0.9))
c
dev.off()
c

# make other more transparent plot
pdf("output_figures/LEALCO-BEH2_accuracy_betweenSubjects_partner_pointplot.pdf")
zz <- ggplot(acc_bSubj_partner, aes(y=mean_bSubj, x=partner, group=produced_label, fill=produced_label)) + 
  geom_point(data= acc_wSubj_partner, aes(y=proportion, x=partner, color=produced_label), stat="identity", position=position_jitterdodge(jitter.width=0.1, dodge.width=.9), size=3) + 
  scale_colour_manual(values = pal1) +
    geom_point(stat="identity", color = "black", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Precedent maintenance (proportion)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  theme(legend.title = element_blank()) +
  ylim(0,1) +
    geom_text(aes(label = produced_label), vjust = -2.5, position=position_dodge(0.9))
zz
dev.off()
zz


labels <- data.frame(
  x = c(
    seq(-0.5, -0.25, length.out = 10),
    seq(-0.5, -0.25, length.out = 11)
  ),
  label = c(
    format(seq(-0.5, -0.25, length.out = 10), digits = 2),
    paste0("\n", LETTERS[1:11])
  )
)
```

## By Subject (Partner x Label x Test Order)

```{r}
# aggregte (within subject)
acc_wSubj_partner <- data_2labels %>%
 filter(!subjID %in%  exclusion_acc) %>%
 group_by(subjID, partner, produced_label, training_order, .drop=FALSE) %>%
  summarize(n=n())

# calculate proportions 
counts <- data_2labels %>%
 filter(!subjID %in%  exclusion_acc) %>%
 group_by(subjID, partner,  training_order, .drop=FALSE) %>%
  summarize(n_total=n())
acc_wSubj_partner <- merge(x=acc_wSubj_partner,y=counts, 
             by=c("subjID", "partner", "training_order"))
acc_wSubj_partner$proportion <- acc_wSubj_partner$n/acc_wSubj_partner$n_tot

# add correctness
acc_wSubj_partner$correct <- "other"
acc_wSubj_partner$correct[acc_wSubj_partner$partner == 'A' & acc_wSubj_partner$produced_label == 'label_A'] <- "matched"
acc_wSubj_partner$correct[acc_wSubj_partner$partner == 'B' & acc_wSubj_partner$produced_label == 'label_B'] <- "matched"
acc_wSubj_partner$correct[acc_wSubj_partner$partner == 'A' & acc_wSubj_partner$produced_label == 'label_A'] <- "matched"
acc_wSubj_partner$correct[acc_wSubj_partner$partner == 'B' & acc_wSubj_partner$produced_label == 'label_B'] <- "matched"
acc_wSubj_partner$correct[acc_wSubj_partner$partner == 'A' & acc_wSubj_partner$produced_label == 'label_B'] <- "non-matched"
acc_wSubj_partner$correct[acc_wSubj_partner$partner == 'B' & acc_wSubj_partner$produced_label == 'label_A'] <- "non-matched"

# aggregte (between subject)
acc_bSubj_partner <- acc_wSubj_partner %>%
  group_by(partner, produced_label, training_order, correct) %>%
  summarise(mean_bSubj = mean(proportion, na.rm=TRUE), sd_bSubj=sd(proportion, na.rm=TRUE), sem_bSubj=(sd(proportion, na.rm=TRUE)/sqrt((length(proportion)))), n_bSubj=length(proportion))



# save
#write.csv(acc_bSubj_partner, "output_stats/LEALCO-BEH2_accuracy_betweenSubjects_partner.csv", row.names = FALSE)

# plot (within subject)
#pdf("output_figures/LEALCO-BEH2_accuracy_betweenSubjects_partner_barplot.pdf")
c <- ggplot(acc_bSubj_partner, aes(y=mean_bSubj, x=partner, group=produced_label, fill=produced_label)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  scale_fill_manual(values = pal1) +
  labs(y="Precedent maintenance (proportion)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  theme(legend.title = element_blank()) +
  ylim(0,1) +
  facet_wrap(~training_order)
c
#dev.off()


```

### LMM (binomial)

Here, we run a first model. Note that our dependent variable (the type of label produced by the subjects) is a categorical variable with 3 levels (label A, label B, other). LMMs are not naturally made to handle DVs with more than 2 levels (but see [here](https://stackoverflow.com/questions/76623653/mixed-effect-multinomial-logistic-regression-model-in-r-non-bayesian-approach) and [here](https://cran.r-project.org/web/packages/multpois/index.html) for possible solutions). For this reason, we run a first model where we "drop" the level "other".

Prepare the ACC data for LMMs.

```{r}
# for each trial, cretae new variable containing the perceived quality of teamwork, dependin gon the current partner (this just takes the correct value from the debfirefing questionnaire, depending on which partner the trial took place with)
#data_trained$team  <- ifelse(data_trained$partner == 'A', data_trained$T101, #data_trained$T201)

# select data
acc_binomial <- data_2labels %>%
  filter(!subjID %in%  exclusion_acc) %>%
  filter(correct != 'other')

# drop levels that are not present in the data
acc_binomial$produced_label <- droplevels(acc_binomial$produced_label)
acc_binomial$produced_label <- fct_relevel(acc_binomial$produced_label, "label_B", "label_A")

# Set sum contrasts for all variables.
contrasts(acc_binomial$test_partner) <- contr.sum(2)
contrasts(acc_binomial$produced_label) <- contr.sum(2)
contrasts(acc_binomial$block)  <- contr.sum(2)
contrasts(acc_binomial$primacy)  <- contr.sum(2)
contrasts(acc_binomial$training_order)  <- contr.sum(2)


# check contrasts
contrasts(acc_binomial$test_partner)
contrasts(acc_binomial$produced_label)
contrasts(acc_binomial$block)
contrasts(acc_binomial$primacy)
contrasts(acc_binomial$recency)
contrasts(acc_binomial$training_order) 

# center continious covariates
acc_binomial <- acc_binomial %>%
  mutate(c_norm = norm - mean(norm, na.rm=TRUE))
```

Try to find the maximally convergent model by using the *buildmer()* approach.

```{r}
# indicate the maximal effect srucutre (both fixed and random) that is motivated based on design & hypotheses
f <- produced_label ~ test_partner*block * training_order * c_norm +
     (test_partner*produced_label*block * training_order | subjID) +
     (test_partner*produced_label*block * training_order  | target_label)

# select the maximal model that still converges
m_acc <- buildmer(f,family=binomial, data=acc_binomial,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_acc)

sink("output_stats/LEALCO-BEH2_acc_lmm.txt")
print(summary(m_acc))
sink()  # returns output to the console
save_model_to_html(m_acc@model, 3 , 'LEALCO-BEH2_acc_lmm.html')

```

Make usual sanity checks for the winning model.

```{r}
# qqplot
pdf("output_figures/LEALCO-BEH2_acc_lmm_qqplot.pdf")
qqnorm(residuals(m_acc))
dev.off()

# histogram
pdf("output_figures/LEALCO-BEH2_acc_lmm_hist.pdf")
hist(residuals(m_acc))
dev.off()

# standardized residuals
pdf("output_figures/LEALCO-BEH2_acc_lmm_residuals.pdf")
plot(residuals(m_acc))
dev.off()
```

### \> Post-hoc / marginal means for (Partner Type x Norm)

Note, that Norms do not refer to the word that was *supposed* to be said 8aka the word matching the partner) but to the word that was actually said. Note also that Norms are NOt normally distributed: most of the norms are below 0.2.

What this analysis says is that some rare tangrams (regardless which partner they were assigned to) had one of the two labels with such high norms, that this norm prevailed over the partner manipulation. So the data on the right side of each graph (high naming norms) represents cases where participants stuck to that high norm label all the time,. In 50% of the cases the label matched the curren tpartner, but in 50% it mismatched, resulting in this 0% scored with large error bars.

```{r}
m_acc.emm_none_partner_norm <-emmeans(m_acc@model, pairwise ~ c_norm * test_partner, adjust = "none", cov.reduce = function(x) quantile(x, c(0.1, 0.25, 0.5, 0.75, 0.9)))


# extract and save marginal means
m_acc.mm_partner_norm <- as.data.frame(m_acc.emm_none_partner_norm$emmeans)
m_acc.mm_partner_norm$emmean_untrans <- plogis(m_acc.mm_partner_norm$emmean) *100
m_acc.mm_partner_norm$asymp.LCL_untrans <- plogis(m_acc.mm_partner_norm$asymp.LCL) *100
m_acc.mm_partner_norm$asymp.UCL_untrans <- plogis(m_acc.mm_partner_norm$asymp.UCL) *100

# save them
write.csv(m_acc.mm_partner_norm,"output_stats/LEALCO-BEH2_acc_binomial_lmm_marginalMeans_partner_norm.csv", row.names = FALSE)

# visualize marginal means
pdf("output_figures/LEALCO-BEH2_acc_binomial_lmm_marginal_partner_norm_pointplot.pdf")
tt <- ggplot(m_acc.mm_partner_norm, aes(y=emmean_untrans, x=c_norm, group=test_partner)) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(0.05), size=3) +
  geom_errorbar(aes(ymin=asymp.LCL_untrans, ymax=asymp.UCL_untrans), width=.1, position=position_dodge(.05)) +
  labs(y="Label Maintenance\n(%)", x="Naming Norms") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,100) +
  facet_wrap(~test_partner)
tt
dev.off()
tt
```

### \> Post-hoc / marginal means (Test Partner)

```{r}
# make post-hoc with no correction
m_acc.emm_none_partner <-emmeans(m_acc@model, pairwise ~ test_partner, adjust = "none")
m_acc.ph_none_partner <- as.data.frame(m_acc.emm_none_partner$contrasts)
write.csv(m_acc.emm_none_partner,"output_stats/LEALCO-BEH2_acc_binomial_ph_none_testpartner.csv", row.names = FALSE)

# extract and save marginal means
m_acc.mm_partner <- as.data.frame(m_acc.emm_none_partner$emmeans)
m_acc.mm_partner$emmean_untrans <- plogis(m_acc.mm_partner$emmean)
m_acc.mm_partner$asymp.LCL_untrans <- plogis(m_acc.mm_partner$asymp.LCL)
m_acc.mm_partner$asymp.UCL_untrans <- plogis(m_acc.mm_partner$asymp.UCL)

# furtner process them
m_acc.mm_partner$produced_label <- 'label_A'
m_acc.mm_partnerB <- m_acc.mm_partner 
m_acc.mm_partnerB$produced_label <- 'label_B'
m_acc.mm_partnerB$emmean_untrans <- 1 - m_acc.mm_partnerB$emmean_untrans
m_acc.mm_partnerB$asymp.LCL_untrans <- 1 - m_acc.mm_partner$asymp.UCL_untrans
m_acc.mm_partnerB$asymp.UCL_untrans <- 1 - m_acc.mm_partner$asymp.LCL_untrans
m_acc.mm_partner <- rbind(m_acc.mm_partner, m_acc.mm_partnerB)
m_acc.mm_partner$emmean_untrans <- m_acc.mm_partner$emmean_untrans  *100
m_acc.mm_partner$asymp.LCL_untrans <- m_acc.mm_partner$asymp.LCL_untrans * 100
m_acc.mm_partner$asymp.UCL_untrans <- m_acc.mm_partner$asymp.UCL_untrans * 100

# save them
write.csv(m_acc.mm_partner,"output_stats/LEALCO-BEH2_acc_binomial_lmm_marginalMeans_partner.csv", row.names = FALSE)

# plot
tt <- ggplot(m_acc.mm_partner, aes(y=emmean_untrans, x=test_partner, group=produced_label, col=produced_label)) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(.3), size=3) +
  geom_errorbar(aes(ymin=asymp.LCL_untrans, ymax=asymp.UCL_untrans), width=.2, position=position_dodge(.3)) +
  labs(y="Label Maintenance\n(%)", x="Partner") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,100) 
ggsave("output_figures/LEALCO-BEH2_acc_binomial_lmm_marginal_labelall_partner_pointplot.pdf", width=4.5
       , height=3.5)
tt

# stacked bar plot (to be reworked)
# tt <- ggplot(m_acc.mm_partner, aes(y=emmean_untrans, x=test_partner, group=test_partner, fill=produced_label)) +
#   scale_colour_manual(values = pal1) +
#   geom_bar(stat="identity", color="black") +
#   geom_point(stat="identity", position=position_dodge(.9), size=3) +
#   geom_errorbar(aes(ymin=asymp.LCL_untrans, ymax=asymp.UCL_untrans), width=.2, position=position_dodge(.9)) +
#   labs(y="Label Maintenance\n(%)", x="Partner") +
#   theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
#   ylim(0,100) +
#   scale_fill_manual(values = pal1)
# tt
```

### \> Post-hoc / marginal means (Test Partner x Primacy x Recency)

```{r}
# # make post-hoc with no correction
# m_acc.ph_none_partner <-emmeans(m_acc@model, ~ test_partner * training_order, adjust = "none")
# m_acc.emm_none_partner <- as.data.frame(m_acc.ph_none_partner$contrasts)
# write.csv(m_acc.emm_none_partner,"output_stats/LEALCO-BEH2_acc_ph_none_testpartner_x_order.csv", row.names = FALSE)
# 
# # extract and save marginal means
# m_acc.mm_partner <- as.data.frame(m_acc.emm_none_partner$emmeans)
# m_acc.mm_partner$emmean_untrans <- plogis(m_acc.mm_partner$emmean)
# m_acc.mm_partner$asymp.LCL_untrans <- plogis(m_acc.mm_partner$asymp.LCL)
# m_acc.mm_partner$asymp.UCL_untrans <- plogis(m_acc.mm_partner$asymp.UCL)
# 
# # save them
# write.csv(m_acc.mm_partner,"output_stats/LEALCO-BEH2_acc_lmm_marginalMeans_partner.csv", row.names = FALSE)
# 
# # visualize marginal means
# #pdf("output_figures/LEALCO-BEH2_acc_lmm_marginal_partner_pointplot.pdf")
# tt <- ggplot(m_acc.mm_partner, aes(y=emmean_untrans, x=test_partner, group=primacy      )) +
#   scale_colour_manual(values = pal1) +
#   geom_point(stat="identity", position=position_dodge(.9), size=3) +
#   geom_errorbar(aes(ymin=asymp.LCL_untrans, ymax=asymp.UCL_untrans), width=.2, position=position_dodge(.9)) +
#   labs(y="Production of label B (vs. A)\n(proportion)", x="Partner") +
#   theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
#   ylim(0,1) +
#   facet_grid(recency ~ primacy)
# tt
# #dev.off()
# #tt
```

### LMM (pseudo-multinomial)

The "binomial" approach has the advantage that is allows to directly tets the effect of partner on label_A and label_B which is our core researh question. However, the downside is tht it requires us to completely disregard the "other" responses. A work around is th transform our trinomial DV in three separat e DV which each will be modelleld separately.

Label A and Label B: training_factor tropped from ther by subJect random factors

Also, removing training_factor from the by item random structure "solves" the issue of overfitting (?).

Label Other: c_norm dropped from the fixed structure

```{r}
# select data
acc_multinomial <- data_2labels %>%
  filter(!subjID %in%  exclusion_acc)

# create dummy DVs for each of the levels of our DV
acc_multinomial$dummy_label_A  <- ifelse(acc_multinomial$produced_label == 'label_A', 1, 0)
acc_multinomial$dummy_label_B  <- ifelse(acc_multinomial$produced_label == 'label_B', 1, 0)   
acc_multinomial$dummy_label_other  <- ifelse(acc_multinomial$produced_label == 'other', 1, 0)   


acc_multinomial$dummy_label_A <- as_factor(acc_multinomial$dummy_label_A)
acc_multinomial$dummy_label_B <- as_factor(acc_multinomial$dummy_label_B)
acc_multinomial$dummy_label_other <- as_factor(acc_multinomial$dummy_label_other)

# Set sum contrasts for all variables.
contrasts(acc_multinomial$test_partner) <- contr.sum(2)
contrasts(acc_multinomial$block)  <- contr.sum(2)
contrasts(acc_multinomial$primacy)  <- contr.sum(2)
contrasts(acc_multinomial$recency)  <- contr.sum(2)
contrasts(acc_multinomial$training_order)  <- contr.sum(2)

# check contrasts
contrasts(acc_multinomial$test_partner)
contrasts(acc_multinomial$block)
contrasts(acc_multinomial$primacy)
contrasts(acc_multinomial$recency)
contrasts(acc_multinomial$training_order)

# center continious covariates
acc_multinomial <- acc_multinomial %>%
  mutate(c_norm = norm - mean(norm, na.rm=TRUE))
```

```{r}

# indicate the maximal effect structure (both fixed and random) that is motivated based on design & hypotheses
f <- dummy_label_A ~ test_partner*block * c_norm * training_order+
     (test_partner * block  | subjID) +
     (test_partner * block * training_order | target_label)

# select the maximal model that still converges
m_acc_labelA <- buildmer(f,family=binomial, data=acc_multinomial,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_acc_labelA)

sink("output_stats/LEALCO-BEH2_acc_labelA_lmm.txt")
print(summary(m_acc_labelA))
sink()  # returns output to the console
```

```{r}
# indicate the maximal effect srucutre (both fixend and random) that is motivated based on design & hypotheses
f <- dummy_label_B ~ test_partner*block * training_order * c_norm +
     (test_partner*block  | subjID) +
     (test_partner*block * training_order | target_label)

# select the maximal model that still converges
m_acc_labelB <- buildmer(f,family=binomial, data=acc_multinomial,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_acc_labelB)

sink("output_stats/LEALCO-BEH2_acc_labelB_lmm.txt")
print(summary(m_acc_labelB))
sink()  # returns output to the console

```

```{r}
# indicate the maximal effect srucutre (both fixend and random) that is motivated based on design & hypotheses
f <- dummy_label_other ~ test_partner*block * training_order +
     (test_partner*block | subjID) +
     (test_partner*block * training_order  | target_label)

# select the maximal model that still converges
m_acc_labelother <- buildmer(f,family=binomial, data=acc_multinomial,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_acc_labelother)

sink("output_stats/LEALCO-BEH2_acc_labelother_lmm.txt")
print(summary(m_acc_labelother))
sink()  # returns output to the console
```

### \> Post-hoc / marginal means (Test Partner)

```{r}
# ========= LABEL A ========

# make post-hoc with no correction
m_acc_labelA.emm_none_partner <-emmeans(m_acc_labelA@model, pairwise ~ test_partner, adjust = "none")
m_acc_labelA.ph_none_partner <- as.data.frame(m_acc_labelA.emm_none_partner$contrasts)
write.csv(m_acc_labelA.ph_none_partner,"output_stats/LEALCO-BEH2_acc_labelA_ph_none_testpartner.csv", row.names = FALSE)

# extract and save marginal means
m_acc_labelA.mm_partner <- as.data.frame(m_acc_labelA.emm_none_partner$emmeans)
m_acc_labelA.mm_partner$emmean_untrans <- plogis(m_acc_labelA.mm_partner$emmean)
m_acc_labelA.mm_partner$asymp.LCL_untrans <- plogis(m_acc_labelA.mm_partner$asymp.LCL)
m_acc_labelA.mm_partner$asymp.UCL_untrans <- plogis(m_acc_labelA.mm_partner$asymp.UCL)

# save them
write.csv(m_acc_labelA.mm_partner,"output_stats/LEALCO-BEH2_acc_lmm_marginalMeans_labelA_partner.csv", row.names = FALSE)

# ========= LABEL B ========

# make post-hoc with no correction
m_acc_labelB.emm_none_partner <-emmeans(m_acc_labelB@model, pairwise ~ test_partner, adjust = "none")
m_acc_labelB.ph_none_partner <- as.data.frame(m_acc_labelB.emm_none_partner$contrasts)
write.csv(m_acc_labelB.ph_none_partner,"output_stats/LEALCO-BEH2_acc_labelB_ph_none_testpartner.csv", row.names = FALSE)

# extract and save marginal means
m_acc_labelB.mm_partner <- as.data.frame(m_acc_labelB.emm_none_partner$emmeans)
m_acc_labelB.mm_partner$emmean_untrans <- plogis(m_acc_labelB.mm_partner$emmean)
m_acc_labelB.mm_partner$asymp.LCL_untrans <- plogis(m_acc_labelB.mm_partner$asymp.LCL)
m_acc_labelB.mm_partner$asymp.UCL_untrans <- plogis(m_acc_labelB.mm_partner$asymp.UCL)

# save them
write.csv(m_acc_labelB.mm_partner,"output_stats/LEALCO-BEH2_acc_lmm_marginalMeans_labelB_partner.csv", row.names = FALSE)


# ========= LABEL OTHER ========

# make post-hoc with no correction
m_acc_labelother.emm_none_partner <-emmeans(m_acc_labelother@model, pairwise ~ test_partner, adjust = "none")
m_acc_labelother.ph_none_partner <- as.data.frame(m_acc_labelother.emm_none_partner$contrasts)
write.csv(m_acc_labelother.ph_none_partner,"output_stats/LEALCO-BEH2_acc_labelother_ph_none_testpartner.csv", row.names = FALSE)

# extract and save marginal means
m_acc_labelother.mm_partner <- as.data.frame(m_acc_labelother.emm_none_partner$emmeans)
m_acc_labelother.mm_partner$emmean_untrans <- plogis(m_acc_labelother.mm_partner$emmean)
m_acc_labelother.mm_partner$asymp.LCL_untrans <- plogis(m_acc_labelother.mm_partner$asymp.LCL)
m_acc_labelother.mm_partner$asymp.UCL_untrans <- plogis(m_acc_labelother.mm_partner$asymp.UCL)

# save them
write.csv(m_acc_labelother.mm_partner,"output_stats/LEALCO-BEH2_acc_lmm_marginalMeans_labelother_partner.csv", row.names = FALSE)

# ======== visualize =========

m_acc_labelA.mm_partner$produced_label <- 'label_A'
m_acc_labelB.mm_partner$produced_label <- 'label_B'
m_acc_labelother.mm_partner$produced_label <- 'other'

m_acc_all.mm_partner <- rbind(m_acc_labelA.mm_partner, m_acc_labelB.mm_partner, m_acc_labelother.mm_partner)

m_acc_all.mm_partner <- m_acc_all.mm_partner %>% 
  mutate(match = case_when(test_partner == 'A' & produced_label == 'label_A' ~ "matched",
                           test_partner == 'B' & produced_label == 'label_B' ~ "matched",
                           test_partner == 'A' & produced_label == 'label_B' ~ "non-matched",
                           test_partner == 'B' & produced_label == 'label_A' ~ "non-matched",
                           produced_label == 'other' ~ 'other'))

# visualize marginal means
tt <- ggplot(m_acc_all.mm_partner, aes(y=emmean_untrans, x=test_partner, group=produced_label, col=produced_label)) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(0.5), size=3) +
  geom_errorbar(aes(ymin=asymp.LCL_untrans, ymax=asymp.UCL_untrans), width=.2, position=position_dodge(.5)) +
  labs(y="Precedent Maintenance\n(proportion)", x="Partner") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,1) 
ggsave("output_figures/LEALCO-BEH2_acc_lmm_marginal_labelall_partner_pointplot.pdf", width=4.5
       , height=3.5)
tt
```

### \> Post-hoc / marginal means (Training Order)

```{r}
# ========= LABEL A ========

# make post-hoc with no correction
m_acc_labelA.emm_none_trainingorder <-emmeans(m_acc_labelA@model, pairwise ~ training_order, adjust = "none")
m_acc_labelA.ph_none_trainingorder <- as.data.frame(m_acc_labelA.emm_none_trainingorder$contrasts)
write.csv(m_acc_labelA.ph_none_trainingorder,"output_stats/LEALCO-BEH2_acc_labelA_ph_none_trainingorder.csv", row.names = FALSE)

# extract and save marginal means
m_acc_labelA.mm_trainingorder <- as.data.frame(m_acc_labelA.emm_none_trainingorder$emmeans)
m_acc_labelA.mm_trainingorder$emmean_untrans <- plogis(m_acc_labelA.mm_trainingorder$emmean)
m_acc_labelA.mm_trainingorder$asymp.LCL_untrans <- plogis(m_acc_labelA.mm_trainingorder$asymp.LCL)
m_acc_labelA.mm_trainingorder$asymp.UCL_untrans <- plogis(m_acc_labelA.mm_trainingorder$asymp.UCL)

# save them
write.csv(m_acc_labelA.mm_trainingorder,"output_stats/LEALCO-BEH2_acc_lmm_marginalMeans_labelA_trainingorder.csv", row.names = FALSE)

# ========= LABEL B ========

# make post-hoc with no correction
m_acc_labelB.emm_none_trainingorder <-emmeans(m_acc_labelB@model, pairwise ~ training_order, adjust = "none")
m_acc_labelB.ph_none_trainingorder <- as.data.frame(m_acc_labelB.emm_none_trainingorder$contrasts)
write.csv(m_acc_labelB.ph_none_trainingorder,"output_stats/LEALCO-BEH2_acc_labelB_ph_none_trainingorder.csv", row.names = FALSE)

# extract and save marginal means
m_acc_labelB.mm_trainingorder <- as.data.frame(m_acc_labelB.emm_none_trainingorder$emmeans)
m_acc_labelB.mm_trainingorder$emmean_untrans <- plogis(m_acc_labelB.mm_trainingorder$emmean)
m_acc_labelB.mm_trainingorder$asymp.LCL_untrans <- plogis(m_acc_labelB.mm_trainingorder$asymp.LCL)
m_acc_labelB.mm_trainingorder$asymp.UCL_untrans <- plogis(m_acc_labelB.mm_trainingorder$asymp.UCL)

# save them
write.csv(m_acc_labelB.mm_trainingorder,"output_stats/LEALCO-BEH2_acc_lmm_marginalMeans_labelB_trainingorder.csv", row.names = FALSE)

# ========= LABEL OTHER ========

# make post-hoc with no correction
m_acc_labelother.emm_none_trainingorder <-emmeans(m_acc_labelother@model, pairwise ~ training_order, adjust = "none")
m_acc_labelother.ph_none_trainingorder <- as.data.frame(m_acc_labelother.emm_none_trainingorder$contrasts)
write.csv(m_acc_labelother.ph_none_trainingorder,"output_stats/LEALCO-BEH2_acc_labelother_ph_none_trainingorder.csv", row.names = FALSE)

# extract and save marginal means
m_acc_labelother.mm_trainingorder <- as.data.frame(m_acc_labelother.emm_none_trainingorder$emmeans)
m_acc_labelother.mm_trainingorder$emmean_untrans <- plogis(m_acc_labelother.mm_trainingorder$emmean)
m_acc_labelother.mm_trainingorder$asymp.LCL_untrans <- plogis(m_acc_labelother.mm_trainingorder$asymp.LCL)
m_acc_labelother.mm_trainingorder$asymp.UCL_untrans <- plogis(m_acc_labelother.mm_trainingorder$asymp.UCL)

# save them
write.csv(m_acc_labelother.mm_trainingorder,"output_stats/LEALCO-BEH2_acc_lmm_marginalMeans_labelother_trainingorder.csv", row.names = FALSE)

# ======== visualize =========

m_acc_labelA.mm_trainingorder$produced_label <- 'label_A'
m_acc_labelB.mm_trainingorder$produced_label <- 'label_B'
m_acc_labelother.mm_trainingorder$produced_label <- 'other'

m_acc_all.mm_trainingorder <- rbind(m_acc_labelA.mm_trainingorder, m_acc_labelB.mm_trainingorder, m_acc_labelother.mm_trainingorder)

#m_acc_all.mm_trainingorder <- m_acc_all.mm_trainingorder %>% 
#  mutate(match = case_when(test_partner == 'A' & produced_label == 'label_A' ~ #"matched",
#                           test_partner == 'B' & produced_label == 'label_B' ~ #"matched",
#                           test_partner == 'A' & produced_label == 'label_B' ~ #"non-matched",
#                           test_partner == 'B' & produced_label == 'label_A' ~ #"non-matched",
#                           produced_label == 'other' ~ 'other'))

# visualize marginal means
pdf("output_figures/LEALCO-BEH2_acc_lmm_marginal_labelall_trainingorder_pointplot.pdf")
tt <- ggplot(m_acc_all.mm_trainingorder, aes(y=emmean_untrans, x=training_order, group=produced_label, col=produced_label)) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(0.5), size=3) +
  geom_errorbar(aes(ymin=asymp.LCL_untrans, ymax=asymp.UCL_untrans), width=.2, position=position_dodge(.5)) +
  labs(y="Precedent maintenance\n(proportion)", x="Training Order") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,1) 
tt
dev.off()
tt
```

### \> Post-hoc / marginal means (Test Partner x Naming Norms)

```{r}
# ========= LABEL A ========

# make post-hoc with no correction
m_acc_labelA.emm_none_partner_norm <-emmeans(m_acc_labelA@model, pairwise ~ c_norm * test_partner, adjust = "none", cov.reduce = function(x) quantile(x, c(0, 0.25, 0.5, 0.75, 0.9, 0.95)))

m_acc_labelA.ph_none_partner_norm <- as.data.frame(m_acc_labelA.emm_none_partner_norm$contrasts)
write.csv(m_acc_labelA.ph_none_trainingorder_testpartner,"output_stats/LEALCO-BEH2_acc_labelA_ph_none_partner_norm.csv", row.names = FALSE)

# extract and save marginal means
m_acc_labelA.mm_partner_norm <- as.data.frame(m_acc_labelA.emm_none_partner_norm$emmeans)
m_acc_labelA.mm_partner_norm$emmean_untrans <- plogis(m_acc_labelA.mm_partner_norm$emmean)
m_acc_labelA.mm_partner_norm$asymp.LCL_untrans <- plogis(m_acc_labelA.mm_partner_norm$asymp.LCL)
m_acc_labelA.mm_partner_norm$asymp.UCL_untrans <- plogis(m_acc_labelA.mm_partner_norm$asymp.UCL)

# save them
write.csv(m_acc_labelA.mm_partner_norm,"output_stats/LEALCO-BEH2_acc_lmm_marginalMeans_labelA_partner_norm.csv", row.names = FALSE)

# ========= LABEL B ========

# make post-hoc with no correction
m_acc_labelB.emm_none_partner_norm <-emmeans(m_acc_labelB@model, pairwise ~ c_norm * test_partner, adjust = "none", cov.reduce = function(x) quantile(x, c(0, 0.25, 0.5, 0.75, 0.9, 0.95)))
m_acc_labelB.ph_none_partner_norm <- as.data.frame(m_acc_labelB.emm_none_partner_norm$contrasts)
write.csv(m_acc_labelB.ph_none_trainingorder_testpartner,"output_stats/LEALCO-BEH2_acc_labelB_ph_none_partner_norm.csv", row.names = FALSE)

# extract and save marginal means
m_acc_labelB.mm_partner_norm <- as.data.frame(m_acc_labelB.emm_none_partner_norm$emmeans)
m_acc_labelB.mm_partner_norm$emmean_untrans <- plogis(m_acc_labelB.mm_partner_norm$emmean)
m_acc_labelB.mm_partner_norm$asymp.LCL_untrans <- plogis(m_acc_labelB.mm_partner_norm$asymp.LCL)
m_acc_labelB.mm_partner_norm$asymp.UCL_untrans <- plogis(m_acc_labelB.mm_partner_norm$asymp.UCL)

# save them
write.csv(m_acc_labelB.mm_partner_norm,"output_stats/LEALCO-BEH2_acc_lmm_marginalMeans_labelB_partner_norm.csv", row.names = FALSE)

# ========= LABEL OTHER ========
# This we cannot do with the variable "Label Other" because c_norm was notint he model.

# ======== visualize =========

m_acc_labelA.mm_partner_norm$produced_label <- 'label_A'
m_acc_labelB.mm_partner_norm$produced_label <- 'label_B'

m_acc_labelall.mm_partner_norm <- rbind(m_acc_labelA.mm_partner_norm, m_acc_labelB.mm_partner_norm)

m_acc_labelall.mm_partner_norm$norm <- m_acc_labelall.mm_partner_norm$c_norm + mean(acc_multinomial$norm , na.rm=TRUE)

#m_acc_all.mm_trainingorder <- m_acc_all.mm_trainingorder %>% 
#  mutate(match = case_when(test_partner == 'A' & produced_label == 'label_A' ~ #"matched",
#                           test_partner == 'B' & produced_label == 'label_B' ~ #"matched",
#                           test_partner == 'A' & produced_label == 'label_B' ~ #"non-matched",
#                           test_partner == 'B' & produced_label == 'label_A' ~ #"non-matched",
#                           produced_label == 'other' ~ 'other'))

# visualize marginal means
pdf("output_figures/LEALCO-BEH2_acc_lmm_marginal_labelall_partner_norm_pointplot.pdf")
tt <- ggplot(m_acc_labelall.mm_partner_norm, aes(y=emmean_untrans, x=norm, group=produced_label, col=produced_label)) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(0.05), size=3) +
  geom_errorbar(aes(ymin=asymp.LCL_untrans, ymax=asymp.UCL_untrans), width=.1, position=position_dodge(.05)) +
  labs(y="Precedent maintenance\n(proportion)", x="Naming Norms") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,1) +
  facet_wrap(~test_partner)
tt
dev.off()
tt
```

### \> Post-hoc / marginal means (Traaining Order x Naming Norms)

```{r}
# ========= LABEL A ========

# make post-hoc with no correction
m_acc_labelA.emm_none_trainingorder_norm <-emmeans(m_acc_labelA@model, pairwise ~ c_norm * training_order, adjust = "none", cov.reduce = function(x) quantile(x, c(0, 0.25, 0.5, 0.75, 0.9, 0.95)))

m_acc_labelA.ph_none_trainingorder_norm <- as.data.frame(m_acc_labelA.emm_none_trainingorder_norm$contrasts)
write.csv(m_acc_labelA.ph_none_trainingorder_norm,"output_stats/LEALCO-BEH2_acc_labelA_ph_none_trainingorder_norm.csv", row.names = FALSE)

# extract and save marginal means
m_acc_labelA.mm_trainingorder_norm <- as.data.frame(m_acc_labelA.emm_none_trainingorder_norm$emmeans)
m_acc_labelA.mm_trainingorder_norm$emmean_untrans <- plogis(m_acc_labelA.mm_trainingorder_norm$emmean)
m_acc_labelA.mm_trainingorder_norm$asymp.LCL_untrans <- plogis(m_acc_labelA.mm_trainingorder_norm$asymp.LCL)
m_acc_labelA.mm_trainingorder_norm$asymp.UCL_untrans <- plogis(m_acc_labelA.mm_trainingorder_norm$asymp.UCL)

# save them
write.csv(m_acc_labelA.mm_trainingorder_norm,"output_stats/LEALCO-BEH2_acc_lmm_marginalMeans_labelA_trainingorder_norm.csv", row.names = FALSE)

# ========= LABEL B ========

# make post-hoc with no correction
m_acc_labelB.emm_none_trainingorder_norm <-emmeans(m_acc_labelB@model, pairwise ~ c_norm * training_order, adjust = "none", cov.reduce = function(x) quantile(x, c(0, 0.25, 0.5, 0.75, 0.9, 0.95)))
m_acc_labelB.ph_none_trainingorder_norm <- as.data.frame(m_acc_labelB.emm_none_trainingorder_norm$contrasts)
write.csv(m_acc_labelB.ph_none_trainingorder_testpartner,"output_stats/LEALCO-BEH2_acc_labelB_ph_none_trainingorder_norm.csv", row.names = FALSE)

# extract and save marginal means
m_acc_labelB.mm_trainingorder_norm <- as.data.frame(m_acc_labelB.emm_none_trainingorder_norm$emmeans)
m_acc_labelB.mm_trainingorder_norm$emmean_untrans <- plogis(m_acc_labelB.mm_trainingorder_norm$emmean)
m_acc_labelB.mm_trainingorder_norm$asymp.LCL_untrans <- plogis(m_acc_labelB.mm_trainingorder_norm$asymp.LCL)
m_acc_labelB.mm_trainingorder_norm$asymp.UCL_untrans <- plogis(m_acc_labelB.mm_trainingorder_norm$asymp.UCL)

# save them
write.csv(m_acc_labelB.mm_trainingorder_norm,"output_stats/LEALCO-BEH2_acc_lmm_marginalMeans_labelB_trainingorder_norm.csv", row.names = FALSE)

# ========= LABEL OTHER ========
# This we cannot do with the variable "Label Other" because c_norm was notint he model.

# ======== visualize =========

m_acc_labelA.mm_trainingorder_norm$produced_label <- 'label_A'
m_acc_labelB.mm_trainingorder_norm$produced_label <- 'label_B'

m_acc_labelall.mm_trainingorder_norm <- rbind(m_acc_labelA.mm_trainingorder_norm, m_acc_labelB.mm_trainingorder_norm)

m_acc_labelall.mm_trainingorder_norm$norm <- m_acc_labelall.mm_trainingorder_norm$c_norm + mean(acc_multinomial$norm , na.rm=TRUE)

#m_acc_all.mm_trainingorder <- m_acc_all.mm_trainingorder %>% 
#  mutate(match = case_when(test_partner == 'A' & produced_label == 'label_A' ~ #"matched",
#                           test_partner == 'B' & produced_label == 'label_B' ~ #"matched",
#                           test_partner == 'A' & produced_label == 'label_B' ~ #"non-matched",
#                           test_partner == 'B' & produced_label == 'label_A' ~ #"non-matched",
#                           produced_label == 'other' ~ 'other'))

# visualize marginal means
pdf("output_figures/LEALCO-BEH2_acc_lmm_marginal_labelall_trainingorder_norm_pointplot.pdf")
tt <- ggplot(m_acc_labelall.mm_trainingorder_norm, aes(y=emmean_untrans, x=norm, group=produced_label, col=produced_label)) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(0.05), size=3) +
  geom_errorbar(aes(ymin=asymp.LCL_untrans, ymax=asymp.UCL_untrans), width=.1, position=position_dodge(.05)) +
  labs(y="Precedent maintenance\n(proportion)", x="Naming Norms") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,1) +
  facet_wrap(~training_order)
tt
dev.off()
tt
```

### \> Post-hoc / marginal means (Test Partner x Training Order x Naming Norms)

This is just to better understand the data, but it is not a follow up on any significant interaction.

```{r}
# ========= LABEL A ========

# make post-hoc with no correction
m_acc_labelA.emm_none_partner_trainingorder_norm <-emmeans(m_acc_labelA@model, pairwise ~ c_norm * training_order * test_partner, adjust = "none", cov.reduce = function(x) quantile(x, c(0, 0.25, 0.5, 0.75, 0.9, 0.95)))

m_acc_labelA.ph_none_partner_trainingorder_norm <- as.data.frame(m_acc_labelA.emm_none_partner_trainingorder_norm$contrasts)
write.csv(m_acc_labelA.ph_none_partner_trainingorder_norm,"output_stats/LEALCO-BEH2_acc_labelA_ph_none__partner_trainingorder_norm.csv", row.names = FALSE)

# extract and save marginal means
m_acc_labelA.mm__partner_trainingorder_norm <- as.data.frame(m_acc_labelA.emm_none_partner_trainingorder_norm$emmeans)
m_acc_labelA.mm__partner_trainingorder_norm$emmean_untrans <- plogis(m_acc_labelA.mm__partner_trainingorder_norm$emmean)
m_acc_labelA.mm__partner_trainingorder_norm$asymp.LCL_untrans <- plogis(m_acc_labelA.mm__partner_trainingorder_norm$asymp.LCL)
m_acc_labelA.mm__partner_trainingorder_norm$asymp.UCL_untrans <- plogis(m_acc_labelA.mm__partner_trainingorder_norm$asymp.UCL)

# save them
write.csv(m_acc_labelA.mm__partner_trainingorder_norm,"output_stats/LEALCO-BEH2_acc_lmm_marginalMeans_labelA__partner_trainingorder_norm.csv", row.names = FALSE)

# ========= LABEL B ========


# make post-hoc with no correction
m_acc_labelB.emm_none_partner_trainingorder_norm <-emmeans(m_acc_labelB@model, pairwise ~ c_norm * training_order * test_partner, adjust = "none", cov.reduce = function(x) quantile(x, c(0, 0.25, 0.5, 0.75, 0.9, 0.95)))

m_acc_labelB.ph_none_partner_trainingorder_norm <- as.data.frame(m_acc_labelA.emm_none_partner_trainingorder_norm$contrasts)
write.csv(m_acc_labelB.ph_none_partner_trainingorder_norm,"output_stats/LEALCO-BEH2_acc_labelB_ph_none__partner_trainingorder_norm.csv", row.names = FALSE)

# extract and save marginal means
m_acc_labelB.mm__partner_trainingorder_norm <- as.data.frame(m_acc_labelB.emm_none_partner_trainingorder_norm$emmeans)
m_acc_labelB.mm__partner_trainingorder_norm$emmean_untrans <- plogis(m_acc_labelB.mm__partner_trainingorder_norm$emmean)
m_acc_labelB.mm__partner_trainingorder_norm$asymp.LCL_untrans <- plogis(m_acc_labelB.mm__partner_trainingorder_norm$asymp.LCL)
m_acc_labelB.mm__partner_trainingorder_norm$asymp.UCL_untrans <- plogis(m_acc_labelB.mm__partner_trainingorder_norm$asymp.UCL)

# save them
write.csv(m_acc_labelB.mm__partner_trainingorder_norm,"output_stats/LEALCO-BEH2_acc_lmm_marginalMeans_labelB__partner_trainingorder_norm.csv", row.names = FALSE)

# ========= LABEL OTHER ========
# This we cannot do with the variable "Label Other" because c_norm was notint he model.

# ======== visualize =========

m_acc_labelA.mm__partner_trainingorder_norm$produced_label <- 'label_A'
m_acc_labelB.mm__partner_trainingorder_norm$produced_label <- 'label_B'

m_acc_labelall.mm_partner_trainingorder_norm <- rbind(m_acc_labelA.mm__partner_trainingorder_norm, m_acc_labelB.mm__partner_trainingorder_norm)

m_acc_labelall.mm_partner_trainingorder_norm$norm <- m_acc_labelall.mm_partner_trainingorder_norm$c_norm + mean(acc_multinomial$norm , na.rm=TRUE)

#m_acc_all.mm_trainingorder <- m_acc_all.mm_trainingorder %>% 
#  mutate(match = case_when(test_partner == 'A' & produced_label == 'label_A' ~ #"matched",
#                           test_partner == 'B' & produced_label == 'label_B' ~ #"matched",
#                           test_partner == 'A' & produced_label == 'label_B' ~ #"non-matched",
#                           test_partner == 'B' & produced_label == 'label_A' ~ #"non-matched",
#                           produced_label == 'other' ~ 'other'))

# visualize marginal means
pdf("output_figures/LEALCO-BEH2_acc_lmm_marginal_labelall_partner_trainingorder_norm_pointplot.pdf")
tt <- ggplot(m_acc_labelall.mm_partner_trainingorder_norm, aes(y=emmean_untrans, x=norm, group=produced_label, col=produced_label)) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(0.05), size=3) +
  geom_errorbar(aes(ymin=asymp.LCL_untrans, ymax=asymp.UCL_untrans), width=.1, position=position_dodge(.05)) +
  labs(y="Precedent maintenance\n(proportion)", x="Naming Norms") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,1) +
  facet_wrap(~training_order~test_partner)
tt
dev.off()
tt
```

## Naming latencies at correct trials

### By Subject (congruency)

Here we just have a simple look at naming latencies, while considering only trials that are correct. In a first moment, we just examine naming latencies in their native format, that is without any type of normalization for approximating normality. Note that the data is right-skewed, expected for latency data.

```{r}
# aggregate
vot_wSubj_congruency <- data_2labels %>%
  filter(error =='correct') %>%
  filter(!subjID %in%  exclusion_vot) %>%
  group_by(subjID, correct) %>%
  summarise(mean = mean(VOT), sd=sd(VOT), sem=(sd(VOT)/sqrt((length(VOT)))), n=length(VOT))

# save
write.csv(vot_wSubj_congruency, "output_stats/LEALCO-BEH2_voz_withinSubjects_congruent.csv", row.names = FALSE)

# plot (within subject)
pdf("output_figures/LEALCO-BEH2_vot_withinSubjects_congruent_barplot.pdf")
a <- ggplot(vot_wSubj_congruency, aes(y=mean, x=correct, fill=correct)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal3) +
  labs(y="Naming latencies (ms)", x="Label Type") +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2, position=position_dodge(.9)) +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  ylim(0,NA) +
  facet_wrap(~subjID)
a
dev.off() 
a
```

```{r}
# aggregte (between subject)
vot_bSubj_congruency <- vot_wSubj_congruency %>%
  group_by(correct) %>%
  summarise(mean_bSubj = mean(mean), sd_bSubj=sd(mean), sem_bSubj=(sd(mean)/sqrt((length(mean)))), n_bSubj=length(mean))

# save
write.csv(acc_bSubj_congruency, "output_stats/LEALCO-BEH2_vot_betweenSubjects_congruency.csv", row.names = FALSE)

# plot (within subject)
pdf("output_figures/LEALCO-BEH2_vot_betweenSubjects_congruency_barplot.pdf")
c <- ggplot(vot_bSubj_congruency, aes(y=mean_bSubj, x=correct, fill=correct)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  scale_fill_manual(values = pal3) +
  labs(y="Naming latencies (ms)", x="Label Type") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  theme(legend.title = element_blank()) +
  ylim(0,NA)
c
dev.off()
c

# make other more transparent plot
pdf("output_figures/LEALCO-BEH2_accuracy_betweenSubjects_congruency_pointplot.pdf")
zz <- ggplot(vot_bSubj_congruency, aes(y=mean_bSubj, x=correct, fill=correct)) + 
  geom_point(data= vot_wSubj_congruency, aes(y=mean, x=correct, color=correct), stat="identity", position=position_jitterdodge(jitter.width=0.1, dodge.width=.9), size=3) + 
  scale_colour_manual(values = pal3) +
    geom_point(stat="identity", color = "black", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Label Type") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  theme(legend.title = element_blank()) +
  ylim(0,NA)
zz
dev.off()
zz
```

### By Subjects (Partner x Label)

```{r}
# aggregate
vot_wSubj_partner <- data_2labels %>%
  filter(error =='correct') %>%
  filter(!subjID %in%  exclusion_vot) %>%
  group_by(subjID, test_partner, produced_label, correct) %>%
  summarise(mean = mean(VOT), sd=sd(VOT), sem=(sd(VOT)/sqrt((length(VOT)))), n=length(VOT))

# save
write.csv(vot_wSubj_congruency, "output_stats/LEALCO-BEH2_voz_withinSubjects_partner.csv", row.names = FALSE)

# plot (within subject)
pdf("output_figures/LEALCO-BEH2_vot_withinSubjects_congruent_barplot.pdf")
a <- ggplot(vot_wSubj_partner, aes(y=mean, x=test_partner, group =produced_label, fill=produced_label)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  labs(y="Naming latencies (ms)", x="Label Type") +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2, position=position_dodge(.9)) +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,NA) +
  geom_text(aes(label = produced_label), vjust = -2.5, position=position_dodge(0.9)) +
  facet_wrap(~subjID)
a
dev.off() 
a
```

```{r}

# aggregate (between subject)
vot_bSubj_partner <- vot_wSubj_partner %>%
  group_by(test_partner, produced_label, correct) %>%
  summarise(mean_bSubj = mean(mean), sd_bSubj=sd(mean), sem_bSubj=(sd(mean)/sqrt((length(mean)))), n_bSubj=length(mean))

# save
write.csv(vot_bSubj_partner, "output_stats/LEALCO-BEH2_vot_betweenSubjects_partner.csv", row.names = FALSE)

# plot (barplot)
pdf("output_figures/LEALCO-BEH2_vot_betweenSubjects_partner_barplot.pdf")
c <- ggplot(vot_bSubj_partner, aes(y=mean_bSubj, x=test_partner, group=produced_label,fill=produced_label)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,2700) +
  geom_text(aes(label = produced_label), vjust = -2.5, position=position_dodge(0.9))
c
dev.off()
c

# plot (raincloud)
pdf("output_figures/LEALCO-BEH2_vot_betweenSubjects_partner_pointplot.pdf")
tt <- ggplot(vot_bSubj_partner, aes(y=mean_bSubj, x=test_partner, group=produced_label,fill=produced_label)) +
  geom_point(data= vot_wSubj_partner, aes(y=mean, x=test_partner, color=correct), stat="identity", position=position_jitterdodge(jitter.width=0.1, dodge.width=.9), size=3) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", color = "black", position=position_dodge(0.9), size=3) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,2700) +
  geom_text(aes(label = produced_label), vjust = -2.5, position=position_dodge(0.9))
tt
dev.off()
tt
```

### LMM

Prepare the VOT data for LMMs. Note that we will be running he model on inverted naming latency (1/naming latency). This results in the magnitude of the datapoints being inverted. The estimates of the models have to be read accordingly.

```{r}

# select data
votINV <- data_2labels %>%
  filter(error == 'correct') %>%
  filter(!subjID %in%  exclusion_vot)

# drop levels that are not present in the data
votINV$produced_label <- droplevels(votINV$produced_label)

# Set sum contrasts for all variables.
contrasts(votINV$test_partner) <- contr.sum(2)
contrasts(votINV$produced_label) <- contr.sum(2)
contrasts(votINV$block)  <- contr.sum(2)
contrasts(votINV$primacy)  <- contr.sum(2)
contrasts(votINV$recency)  <- contr.sum(2)
contrasts(votINV$training_order)  <- contr.sum(2)

# check contrasts
contrasts(votINV$test_partner)
contrasts(votINV$produced_label)
contrasts(votINV$block)
contrasts(votINV$primacy)
contrasts(votINV$recency)
contrasts(votINV$training_order)

# center continious covariates
votINV <- votINV %>%
  mutate(c_norm = norm - mean(norm, na.rm=TRUE))
```

Try to find the maximally convergent model by using the *buildmer()* approach.

```{r}

# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- VOTinv ~ test_partner*produced_label*block * training_order * c_norm +
     (test_partner*produced_label*block  | subjID) +
     (test_partner*produced_label*block * training_order  | target_label)

# select the maximal model that still converges
m_votINV <- buildmer(f,data=votINV,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_votINV)

# save output
sink("output_stats/LEALCO-BEH2_votINV_lmm.txt")
print(summary(m_votINV))
sink()  # returns output to the console
save_model_to_html(m_votINV@model, 6, 'LEALCO-BEH2_votINV_lmm.html')

```

Make model sanity checks. Everything seems ok.

```{r}
# qqplot
pdf("output_figures/LEALCO-BEH2_votINV_lmm_qqplot.pdf")
qqnorm(residuals(m_votINV))
dev.off()

# histogram
pdf("output_figures/LEALCO-BEH2_votINV_lmm_hist.pdf")
hist(residuals(m_votINV))
dev.off()

# standardized residuals
pdf("output_figures/LEALCO-BEH2_votINV_lmm_residuals.pdf")
plot(residuals(m_votINV))
dev.off()
```

### Post-hoc / marginal means (Block)

```{r}

# make post-hoc with no correction
m_votINV.emm_none_block <-emmeans(m_votINV@model, pairwise ~ block, adjust = "none")
m_votINV.ph_none_block <- as.data.frame(m_votINV.emm_none_block$contrasts)
write.csv(m_votINV.ph_none_block,"output_stats/LEALCO-BEH2_votINV_ph_none_block.csv", row.names = FALSE)

# extract and save marginal means
m_votINV.mm_block <- as.data.frame(m_votINV.emm_none_block$emmeans)
m_votINV.mm_block$emmean_untrans <- 1/m_votINV.mm_block$emmean
m_votINV.mm_block$lower.CL_untrans <- 1/m_votINV.mm_block$upper.CL
m_votINV.mm_block$upper.CL_untrans <- 1/m_votINV.mm_block$lower.CL
write.csv(m_votINV.mm_block,"output_stats/LEALCO-BE2H_votINV_lmm_marginal_block.csv", row.names = FALSE)

# plot
pdf("output_figures/LEALCO-BEH2_votINV_lmm_marginal_block_pointplot.pdf")
tt <- ggplot(m_votINV.mm_block, aes(y=emmean_untrans, x=block)) +
  #scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=lower.CL_untrans, ymax=upper.CL_untrans), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,NA)
tt
dev.off()
tt
```

### Post-hoc / marginal means for (Partner Type x Norm)

```{r}
# make post-hoc with tukey correction
m_votINV.emm_tukey_partner_x_norm <-emmeans(m_votINV@model, pairwise ~ test_partner * c_norm, adjust = "Tukey", cov.reduce = function(x) quantile(x, c(0, 0.5, 1)))
m_votINV.ph_tukey_partner_x_norm <- as.data.frame(m_votINV.emm_tukey_partner_x_norm$contrasts)
write.csv(m_votINV.emm_tukey_partner_x_norm,"output_stats/LEALCO-BEH2_votINV_ph_tukey_partner_x_norm.csv", row.names = FALSE)

# make post-hoc with no correction
m_votINV.emm_none_partner_x_norm <-emmeans(m_votINV@model, pairwise ~ test_partner * c_norm, adjust = "none", cov.reduce = function(x) quantile(x, c(0, 0.5,  1)))
m_votINV.ph_none_partner_x_norm <- as.data.frame(m_votINV.emm_none_partner_x_norm$contrasts)
write.csv(m_votINV.emm_none_partner_x_norm,"output_stats/LEALCO-BEH2_votINV_ph_none_partner_x_norm.csv", row.names = FALSE)

# extract and save marginal means
m_votINV.mm_partner_x_norm <- as.data.frame(m_votINV.emm_tukey_partner_x_norm$emmeans)
m_votINV.mm_partner_x_norm$emmean_untrans <- 1/m_votINV.mm_partner_x_norm$emmean
m_votINV.mm_partner_x_norm$lower.CL_untrans <- 1/m_votINV.mm_partner_x_norm$upper.CL
m_votINV.mm_partner_x_norm$upper.CL_untrans <- 1/m_votINV.mm_partner_x_norm$lower.CL
write.csv(m_votINV.mm_partner_x_norm,"output_stats/LEALCO-BEH2_votINV_lmm_marginal_partner_x_norm.csv", row.names = FALSE)

# plot
p <- ggplot(m_votINV.mm_partner_x_norm, aes(x=c_norm, y=emmean_untrans , color=test_partner, group=test_partner)) +
  geom_point(stat = "identity", position=position_dodge(0.05)) +
  geom_errorbar(aes(ymin=emmean_untrans-SE, ymax=emmean_untrans+SE), width=.1, position=position_dodge(0.05)) +
  #geom_ribbon(aes(ymin=LCL, ymax=UCL, fill=partner_type), alpha=.5) +
  scale_fill_manual(values = pal1) +
  scale_color_manual(values = pal1) +
  labs(y="Naming Latencies (ms)", x="Naming Norms (centered)") +
  #ylim(-4, 20) +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) 
p
ggsave("output_figures/LEALCO-BEH2_votINV_partner_x_norm_.pdf")
```

```{r}
# generate predicted data (but don't plot it yet with emmip)
(mylist <- list(c_norm=c(min(votINV$c_norm), mean(votINV$c_norm), max(votINV$c_norm)), test_partner=c("A","B")))

(mylist <- list(c_norm=c(seq(min(votINV$c_norm), max(votINV$c_norm), 0.05)), test_partner=c("A","B")))

m_votINV.emm_none_partner_x_norm <- emmip(m_votINV@model, c_norm ~ training_order, at=mylist,CIs=TRUE, plotit=FALSE)

m_votINV.emm_none_trainingorder_x_norm <- emmip(m_votINV@model, c_norm ~ training_order, plotit=FALSE)

m_votINV.emm_none_trainingorder_x_norm

#P200_marginalMeans <- as.data.frame(emm_tukey$emmeans)
write.csv(P200_marginalMeans,"output_stats/LEALCO-BEH2_votING_lmm_marginal_trainingorder_x_norm.csv", row.names = FALSE)

# plot
pdf("output_figures/LEALCO-BEH2_votING_lmm_marginal_trainingorder_x_norm.pdf")
ggplot(m_votINV.emm_none_partner_x_norm, aes(x=c_norm, y=yvar, color=training_order, group=training_order))+
  geom_line() +
  geom_ribbon(aes(ymin=LCL, ymax=UCL, fill=training_order), alpha=.5) +
  scale_fill_manual(values = pal1) +
  scale_color_manual(values = pal1) +
  #facet_grid(~block) +
  labs(y="Naming Latencies (uV)", x="Norms (centered)") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16))
dev.off()
```

### Post-hoc / marginal means for (Partner Type x Label)

Compute post-hoc tests and export.

```{r}
# make post-hoc with tukey correction
m_votINV.emm_tukey_partner_x_label <-emmeans(m_votINV@model, pairwise ~ test_partner * produced_label, adjust = "tukey")
m_votINV.ph_tukey_partner_x_label <- as.data.frame(m_votINV.emm_tukey_partner_x_label$contrasts)
write.csv(m_votINV.ph_tukey_partner_x_label,"output_stats/LEALCO-BEH2_votINV_ph_tukey_partner_x_label.csv", row.names = FALSE)

# make post-hoc with no correction
m_votINV.emm_none_partner_x_label <-emmeans(m_votINV@model, pairwise ~ test_partner * produced_label, adjust = "none")
m_votINV.ph_none_partner_x_label <- as.data.frame(m_votINV.emm_none_partner_x_label$contrasts)
m_votINV.ph_none_partner_x_label$p.valueBonf2 = m_votINV.ph_none_partner_x_label$p.value *2
m_votINV.ph_none_partner_x_label$p.valueBonf4 = m_votINV.ph_none_partner_x_label$p.value *4
write.csv(m_votINV.ph_none_partner_x_label,"output_stats/LEALCO-BEH2_votINV_ph_none_partner_x_label.csv", row.names = FALSE)

# extract and save marginal means
m_votINV.mm_partner_x_label <- as.data.frame(m_votINV.emm_none_partner_x_label$emmeans)
m_votINV.mm_partner_x_label$emmean_untrans <- 1/m_votINV.mm_partner_x_label$emmean
m_votINV.mm_partner_x_label$lower.CL_untrans <- 1/m_votINV.mm_partner_x_label$upper.CL
m_votINV.mm_partner_x_label$upper.CL_untrans <- 1/m_votINV.mm_partner_x_label$lower.CL
m_votINV.mm_partner_x_label <- m_votINV.mm_partner_x_label %>% 
  mutate(match = case_when(test_partner == 'A' & produced_label == 'label_A' ~ "match",
                           test_partner == 'B' & produced_label == 'label_B' ~ "match",
                           test_partner == 'A' & produced_label == 'label_B' ~ "non-match",
                           test_partner == 'B' & produced_label == 'label_A' ~ "non-match"))
write.csv(m_votINV.mm_partner_x_label,"output_stats/LEALCO-BEH2_votINV_lmm_marginal_partner_x_block.csv", row.names = FALSE)

# plot
tt <- ggplot(m_votINV.mm_partner_x_label, aes(y=emmean_untrans, x=test_partner, group = produced_label, col = produced_label)) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=lower.CL_untrans, ymax=upper.CL_untrans), width=.2, position=position_dodge(.9)) +
  labs(y="Naming Latencies (ms)", x="Partner") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
ylim(0,2000)
ggsave("output_figures/LEALCO-BEH2_votINV_lmm_marginal_partner_x_label_pointplot.pdf", width=4.5 , height=3.5)
tt
```

## Entrainment analysis

The following analysis examines the reaction between Label Maintenance and (inverted) Naming Latency. This is interesting because there could be a speed accuracy trade-off (i.e. entraining with the partner is cognitively costly) or on the contrary it is possible that entraining with the partner is in fact facilitatory.

#### Version 1: based on inverted naming latencies

```{r}
# aggregte accuracy (within subject)
acc_wSubj_match <- acc_wSubj_congruency %>%
  filter(correct %in% c('matching', 'non-matching'))
acc_wSubj_match$n <- NULL

# aggregate VOTinv (within subjects) only for correct trials
votINV_wSubj_match <- data_2labels %>%
  filter(error == 'correct') %>%
  filter(!subjID %in%  exclusion_vot) %>%
  group_by(subjID, correct) %>%
  summarise(mean_VOTinv = mean(VOTinv), mean_VOT = mean(VOT))

# merge the two DVs in one dataframe
entrainment_data <- merge(acc_wSubj_match,votINV_wSubj_match,by=c("subjID","correct"))

# pivot from long to wide
entrainment_data <- entrainment_data %>% 
  pivot_wider(
    names_from = correct, 
    values_from = c(proportion, mean_VOTinv, mean_VOT)
  )

# calculate entrainment scores (same - different)
entrainment_data$entrainment_ACC <- entrainment_data$proportion_matching - entrainment_data$`proportion_non-matching`
entrainment_data$entrainment_VOTinv <- (entrainment_data$mean_VOTinv_matching - entrainment_data$`mean_VOTinv_non-matching`) * 10000
entrainment_data$entrainment_VOT <- (entrainment_data$mean_VOT_matching - entrainment_data$`mean_VOT_non-matching`)

# scatterplot
ggplot(entrainment_data, aes(x=entrainment_VOTinv, y=entrainment_ACC)) +
  geom_point() +
  stat_smooth(method=lm, fullrange=TRUE, color = 'black') + 
  geom_hline(yintercept=0, linetype="dotted") +
  geom_vline(xintercept=0, linetype="dotted") +
  xlim(-5, 5) +
  ylim(-1.5, 1.5) + 
  xlab('Entrainment NL\n(matching vs. mismatching)') +
  ylab('Entrainment LM\n(matching vs. mismatching)') +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=12))
ggsave("output_figures/LEALCO-BEH2_entrainment_correlation_VOTinv.pdf",  width=6, height=3.5)

# correlation
corr <- cor.test(entrainment_data$entrainment_ACC, entrainment_data$entrainment_VOTinv)
sink('output_stats/LEALCO-BEH2_entrainment_correlation_VOTinv.txt')
print(corr)
sink()
```

```{r}

# scatterplot
ggplot(entrainment_data, aes(x=entrainment_VOT, y=entrainment_ACC)) +
  geom_point() +
  stat_smooth(method=lm, fullrange=TRUE, color = 'black') + 
  geom_hline(yintercept=0, linetype="dotted") +
  geom_vline(xintercept=0, linetype="dotted") +
  xlim(-2600, 2600) +
  ylim(-1.5, 1.5) + 
  xlab('Entrainment NL\n(matching vs. mismatching)') +
  ylab('Entrainment LM\n(matching vs. mismatching)') +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=12))
ggsave("output_figures/LEALCO-BEH2_entrainment_correlation_VOTraw.pdf",  width=6, height=3.5)

# correlation
corr <- cor.test(entrainment_data$entrainment_ACC, entrainment_data$entrainment_VOTinv)
sink('output_stats/LEALCO-BEH2_entrainment_correlation_VOTraw.txt')
print(corr)
sink()
```

### Version 2: based on raw naming latencies

```{r}

```

## Error patterns at inaccurate trials

### By Subject (native, partner x block)

First, we need to dummy code our *error* variable so that from an *error* variable with 4 levels, we get four variables (one per error type) with a binary outcome each. This will make it easier to calculate rates for each error type as well as run LMM later.

```{r}
# # make dummy coding
# data_trained$error_1 <- ifelse(data_trained$error == 1, 1, 0)
# data_trained$error_2 <- ifelse(data_trained$error == 2, 1, 0)
# data_trained$error_3 <- ifelse(data_trained$error == 3, 1, 0)
# data_trained$error_4 <- ifelse(data_trained$error == 4, 1, 0)
```

```{r}
# # aggregte (within subject)
# error_acc_wSubj_partner <- data_trained %>%
#   filter(!subjID %in%  c(exclusion_vot, 33))  %>%
#   group_by(subjID, partner_type, block) %>%
#   summarise(compound = mean(error_1),
#             semantically_related = mean(error_2),
#             phonologically_related = mean(error_3),
#             unrelated = mean(error_4))
# 
# # pivot
# error_acc_wSubj_partner <-error_acc_wSubj_partner %>% 
#   pivot_longer(
#     cols = !c(subjID, partner_type, block), 
#     names_to = "error", 
#     values_to = "rate"
#   )
# 
# # save
# write.csv(error_acc_wSubj_partner, "output_stats/LEALCO-BEH_error_acc_withinSubjects_partner.csv", row.names = FALSE)
# 
# # aggregte (between subject)
# error_acc_bSubj_partner <- error_acc_wSubj_partner %>%
#   group_by(partner_type, block, error) %>%
#   summarise(mean_bSubj = mean(rate), sd_bSubj=sd(rate), sem_bSubj=(sd(rate)/sqrt((length(rate)))), n_bSubj=length(rate))
# 
# # save
# write.csv(error_acc_bSubj_partner, "output_stats/LEALCO-BEH_error_acc_betweenSubjects_partner.csv", row.names = FALSE)
```

```{r}

# # plot (within subject)
# pdf("output_figures/LEALCO-BEH_error_acc_betweenSubjects_partner_block_barplot.pdf")
# c <- ggplot(error_acc_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
#   geom_bar(stat="identity", color = "black", position=position_dodge()) +
#   geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
#   scale_fill_manual(values = pal1) +
#   labs(y="Average error rate", x="Block") +
#   theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
#   ylim(0,NA) +
#   facet_grid(error ~ block)
# c
# dev.off()
# c
# 
# # make other more transparent plot
# pdf("output_figures/LEALCO-BEH_error_acc_betweenSubjects_partner_block_pointplot.pdf")
# zz <- ggplot(error_acc_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
#   geom_point(data= error_acc_wSubj_partner, aes(y=rate, x=partner_type, color=partner_type), stat="identity", position = position_jitter(w = 0.05), size=0.8) + 
#   scale_colour_manual(values = pal1) +
#     geom_point(stat="identity", color = "black", position=position_dodge(), size=2) +
#   geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
#   labs(y="Average error rate", x="Block") +
#   theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
#   ylim(0,1) +
#   facet_grid(error ~ block)
# zz
# dev.off()
```

### LMM

```{r}
# # select data
# error_acc <- data_trained %>%
#   #filter(error %in% c(1, 2, 3, 4)) %>%
#   filter(!subjID %in%  c(exclusion_vot, 33))
# 
# # Set sum contrasts for all variables.
# error_acc$partner_type <- droplevels(error_acc$partner_type)
# contrasts(error_acc$partner_type) <- contr.sum(2)
# contrasts(error_acc$block)  <- contr.sum(2)
# 
# # check contrasts
# contrasts(error_acc$partner_type)
# contrasts(error_acc$block)
# 
# # center covariates
# error_acc <- error_acc %>%
#   mutate(c_SUBTLEX_frequency_log = SUBTLEX_frequency_log - mean(SUBTLEX_frequency_log, na.rm=TRUE))
# 
# error_acc <- error_acc %>%
#   mutate(c_FASQUEL_concreteness = FASQUEL_concreteness - mean(FASQUEL_concreteness, na.rm=TRUE))
# 
# error_acc <- error_acc %>%
#   mutate(c_FASQUEL_image_agreement = FASQUEL_image_agreement - mean(FASQUEL_image_agreement, na.rm=TRUE))
# 
# error_acc <- error_acc %>%
#   mutate(team = team - mean(team, na.rm=TRUE))
```

#### Error 1 - compound words

```{r}

# # define maximal model structure
# f <-  error_1 ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
#      (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement + c_FASQUEL_concreteness | subjID) +
#      (partner_type*block | target_label)
# 
# # fit model
# m_error1_acc <- buildmer(f,family=binomial, data=error_acc,buildmerControl=buildmerControl(direction='order',
#           args=list(control=lmerControl(optimizer='bobyqa'))))
# summary(m_error1_acc)
# 
# # save
# sink("output_stats/LEALCO-BEH_error2_acc_lmm.txt")
# print(summary(m_error1_acc))
# sink()  # returns output to the console
```

```{r}
# # make post-hoc with no correction
# m_error1_acc.emm_none_partner <-emmeans(m_error1_acc@model, pairwise ~ partner_type, adjust = "none", pbkrtest.limit = 3201)
# m_error_acc_1.emm_none_partner <- as.data.frame(m_error1_acc.emm_none_partner$contrasts)
# write.csv(m_error1_acc.emm_none_partner,"output_stats/LEALCO-BEH_error1_acc_ph_none_partner.csv", row.names = FALSE)
# 
# # extract and save marginal means
# m_error1_acc.mm_partner <- as.data.frame(m_error1_acc.emm_none_partner$emmeans)
# m_error1_acc.mm_partner$emmean_untrans <- plogis(m_error1_acc.mm_partner$emmean)
# m_error1_acc.mm_partner$lower.CL_untrans <- plogis(m_error1_acc.mm_partner$asymp.LCL)
# m_error1_acc.mm_partner$upper.CL_untrans <- plogis(m_error1_acc.mm_partner$asymp.UCL)
# write.csv(m_error1_acc.mm_partner,"output_stats/LEALCO-BEH_error1_acc_lmm_marginal_partner.csv", row.names = FALSE)
```

```{r}

# # make post-hoc with no correction
# m_error4_acc.emm_none_partner <-emmeans(m_error4_acc@model, pairwise ~ partner_type, adjust = "none", pbkrtest.limit = 3201)
# m_error_acc_4.emm_none_partner <- as.data.frame(m_error4_acc.emm_none_partner$contrasts)
# write.csv(m_error4_acc.emm_none_partner,"output_stats/LEALCO-BEH_error4_acc_ph_none_partner.csv", row.names = FALSE)
# 
# # extract and save marginal means
# m_error4_acc.mm_partner <- as.data.frame(m_error4_acc.emm_none_partner$emmeans)
# m_error4_acc.mm_partner$emmean_untrans <- plogis(m_error4_acc.mm_partner$emmean)
# m_error4_acc.mm_partner$lower.CL_untrans <- plogis(m_error4_acc.mm_partner$asymp.LCL)
# m_error4_acc.mm_partner$upper.CL_untrans <- plogis(m_error4_acc.mm_partner$asymp.UCL)
# write.csv(m_error4_acc.mm_partner,"output_stats/LEALCO-BEH_error4_acc_lmm_marginal_partner.csv", row.names = FALSE)
```

#### Error 2 - semantically related words

```{r}
# # define maximal model structure
# f <-  error_2 ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
#      (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement + c_FASQUEL_concreteness | subjID) +
#      (partner_type*block | target_label)
# 
# # fit model
# m_error2_acc <- buildmer(f,family=binomial, data=error_acc,buildmerControl=buildmerControl(direction='order',
#           args=list(control=lmerControl(optimizer='bobyqa'))))
# summary(m_error2_acc)
# 
# # save
# sink("output_stats/LEALCO-BEH_error2_acc_lmm.txt")
# print(summary(m_error2_acc))
# sink()  # returns output to the console
```

```{r}
# # make post-hoc with no correction
# m_error2_acc.emm_none_partner <-emmeans(m_error2_acc@model, pairwise ~ partner_type, adjust = "none", pbkrtest.limit = 3201)
# m_error_acc_2.emm_none_partner <- as.data.frame(m_error2_acc.emm_none_partner$contrasts)
# write.csv(m_error2_acc.emm_none_partner,"output_stats/LEALCO-BEH_error2_acc_ph_none_partner.csv", row.names = FALSE)
# 
# # extract and save marginal means
# m_error2_acc.mm_partner <- as.data.frame(m_error2_acc.emm_none_partner$emmeans)
# m_error2_acc.mm_partner$emmean_untrans <- 1/m_error2_acc.mm_partner$emmean
# m_error2_acc.mm_partner$lower.CL_untrans <- 1/m_error2_acc.mm_partner$asymp.LCL)
# m_error2_acc.mm_partner$upper.CL_untrans <- plogis(m_error2_acc.mm_partner$asymp.UCL)
# write.csv(m_error2_acc.mm_partner,"output_stats/LEALCO-BEH_error2_acc_lmm_marginal_partner.csv", row.names = FALSE)
```

#### Error 4 - unrelated words

```{r}
# # define maximal model structure
# f <-  error_4 ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
#      (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement + c_FASQUEL_concreteness | subjID) +
#      (partner_type*block | target_label)
# 
# # fit model
# m_error4_acc <- buildmer(f,family=binomial, data=error_acc,buildmerControl=buildmerControl(direction='order',
#           args=list(control=lmerControl(optimizer='bobyqa'))))
# summary(m_error4_acc)
# 
# # save
# sink("output_stats/LEALCO-BEH_error4_acc_lmm.txt")
# print(summary(m_error4_acc))
# sink()  # returns output to the console
```

```{r}

# # make post-hoc with no correction
# m_error4_acc.emm_none_partner <-emmeans(m_error4_acc@model, pairwise ~ partner_type, adjust = "none", pbkrtest.limit = 3201)
# m_error_acc_4.emm_none_partner <- as.data.frame(m_error4_acc.emm_none_partner$contrasts)
# write.csv(m_error4_acc.emm_none_partner,"output_stats/LEALCO-BEH_error4_acc_ph_none_partner.csv", row.names = FALSE)
# 
# # extract and save marginal means
# m_error4_acc.mm_partner <- as.data.frame(m_error4_acc.emm_none_partner$emmeans)
# m_error4_acc.mm_partner$emmean_untrans <- plogis(m_error4_acc.mm_partner$emmean)
# m_error4_acc.mm_partner$lower.CL_untrans <- plogis(m_error4_acc.mm_partner$asymp.LCL)
# m_error4_acc.mm_partner$upper.CL_untrans <- plogis(m_error4_acc.mm_partner$asymp.UCL)
# write.csv(m_error4_acc.mm_partner,"output_stats/LEALCO-BEH_error4_acc_lmm_marginal_partner.csv", row.names = FALSE)
```

```{r}
# # plot
# pdf("output_figures/LEALCO-BEH_error_acc_lmm_marginal_partner.pdf",  width=10, height=3)
# p1 <- ggplot(m_error1_acc.mm_partner, aes(y=emmean_untrans, x=partner_type, color=partner_type)) + 
#   scale_colour_manual(values = pal1) +
#   geom_point(stat="identity", position=position_dodge(.9), size=3) +
#   geom_errorbar(aes(ymin=lower.CL_untrans, ymax=upper.CL_untrans), width=.2, position=position_dodge(.9)) +
#   labs(y="Compounded novel labels\n(proportion)", x="Partner Type") +
#   theme(axis.text=element_text(size=10), axis.title=element_text(size=12)) +
#   ylim(0,1) 
# 
# p2 <- ggplot(m_error2_acc.mm_partner, aes(y=emmean_untrans, x=partner_type, color=partner_type)) + 
#   scale_colour_manual(values = pal1) +
#   geom_point(stat="identity", position=position_dodge(.9), size=3) +
#   geom_errorbar(aes(ymin=lower.CL_untrans, ymax=upper.CL_untrans), width=.2, position=position_dodge(.9)) +
#   labs(y="Semantically related novel labels\n(proportion)", x="Partner Type") +
#   theme(axis.text=element_text(size=10), axis.title=element_text(size=12)) +
#   ylim(0,1)
# 
# p4 <- ggplot(m_error4_acc.mm_partner, aes(y=emmean_untrans, x=partner_type, color=partner_type)) + 
#   scale_colour_manual(values = pal1) +
#   geom_point(stat="identity", position=position_dodge(.9), size=3) +
#   geom_errorbar(aes(ymin=lower.CL_untrans, ymax=upper.CL_untrans), width=.2, position=position_dodge(.9)) +
#   labs(y="Unrelated novel labels\n(proportion)", x="Partner Type") +
#   theme(axis.text=element_text(size=10), axis.title=element_text(size=12)) +
#   ylim(0,1)
# 
# grid.arrange(p1, p2, p4,ncol=3)
# 
# dev.off()  
# #tt
```

## Naming latencies at inaccurate trials

### By Subject (native, partner x block)

```{r}
# # aggregte (within subject)
# error_vot_wSubj_partner <- data_trained %>%
#   filter(error %in% c(1,2,3,4)) %>%
#   filter(!subjID %in%  c(exclusion_vot, 33))  %>%
#   group_by(subjID, partner_type, block, error) %>%
#   summarise(mean = mean(VOT), sd=sd(VOT), sem=(sd(VOT)/sqrt((length(VOT)))), n=length(VOT))
# 
# # rename the errors (for better graph legibility)
# error_vot_wSubj_partner$error <- recode(error_vot_wSubj_partner$error,
#                                        '1' = 'compound', 
#                                        '2' = 'semantically_related',
#                                        '3' = 'phonologically_related',
#                                        '4' = 'unrelated')
# 
# # save
# write.csv(error_vot_wSubj_partner, "output_stats/LEALCO-BEH_error_vot_withinSubjects_partner_block.csv", row.names = FALSE)
# 
# error_vot_bSubj_partner <- error_vot_wSubj_partner %>%
#   group_by(partner_type, block, error) %>%
#   summarise(mean_bSubj = mean(mean), sd_bSubj=sd(mean), sem_bSubj=(sd(mean)/sqrt((length(mean)))), n_bSubj=length(mean))
# 
# # save
# write.csv(error_vot_bSubj_partner, "output_stats/LEALCO-BEH_error_vot_betweenSubjects_partner_block.csv", row.names = FALSE)

```

```{r}

# # reorder the factor levels (so that they are shown in the right order in the plot)
# error_vot_bSubj_partner$error <- factor(error_vot_bSubj_partner$error, levels = c("correct", "compound", "semantically_related", "phonologically_related", "unrelated", "5", "6", "8", "9", "0"))
# 
# # plot (within subject)
# pdf("output_figures/LEALCO-BEH_error_vot_betweenSubjects_partner_block_barplot.pdf")
# c <- ggplot(error_vot_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
#   geom_bar(stat="identity", color = "black", position=position_dodge()) +
#   geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
#   scale_fill_manual(values = pal1) +
#   labs(y="Naming latencies (ms)", x="Block") +
#   theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
#   ylim(0,NA) +
#   facet_grid(error ~ block)
# c
# dev.off()
# c
# 
# # make other more transparent plot
# pdf("output_figures/LEALCO-BEH_error_vot_betweenSubjects_partner_block_pointplot.pdf")
# zz <- ggplot(error_vot_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
#   geom_point(data= error_vot_wSubj_partner, aes(y=mean, x=partner_type, color=partner_type), stat="identity", position = position_jitter(w = 0.05), size=1) + 
#   scale_colour_manual(values = pal1) +
#     geom_point(stat="identity", color = "black", position=position_dodge(), size=2) +
#   geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
#   labs(y="Naming latencies (ms)", x="Block") +
#   theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
#   ylim(0,NA) +
#   facet_grid(error ~ block)
# zz
# dev.off()
# zz
```

### LMM

First select all error trials

```{r}
# # select data
# error_votINV <- data_trained %>%
#   filter(error %in% c(1, 2, 3, 4)) %>%
#   filter(!subjID %in%  c(exclusion_vot, 33))
# 
# # Set sum contrasts for all variables.
# error_votINV$partner_type <- droplevels(error_votINV$partner_type)
# contrasts(error_votINV$partner_type) <- contr.sum(2)
# contrasts(error_votINV$block)  <- contr.sum(2)
# 
# # check contrasts
# contrasts(error_votINV$partner_type)
# contrasts(error_votINV$block)
# 
# # center covariates
# error_votINV <- error_votINV %>%
#   mutate(c_SUBTLEX_frequency_log = SUBTLEX_frequency_log - mean(SUBTLEX_frequency_log, na.rm=TRUE))
# 
# error_votINV <- error_votINV %>%
#   mutate(c_FASQUEL_concreteness = FASQUEL_concreteness - mean(FASQUEL_concreteness, na.rm=TRUE))
# 
# error_votINV <- error_votINV %>%
#   mutate(c_FASQUEL_image_agreement = FASQUEL_image_agreement - mean(FASQUEL_image_agreement, na.rm=TRUE))
# 
# error_votINV <- error_votINV %>%
#   mutate(team = team - mean(team, na.rm=TRUE))
```

Indicate the maximal effect structure (both fixed and random) that is motivated based on design & hypotheses.

```{r}
# f <- VOTinv ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
#      (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement + c_FASQUEL_concreteness | subjID) +
#      (partner_type*block | target_label)

```

#### Error 1- compound words

```{r}

# error1_votINV <- error_votINV %>%
#   filter (error == 1)
# m_error1_votINV <- buildmer(f,data=error1_votINV,buildmerControl=buildmerControl(direction='order',
#           args=list(control=lmerControl(optimizer='bobyqa'))))
# summary(m_error1_votINV)
# 
# # save
# sink("output_stats/LEALCO-BEH_error1_vot_lmm.txt")
# print(summary(m_error1_votINV))
# sink()  # returns output to the console
```

```{r}
# # make post-hoc with no correction
# m_error1_vot.emm_none_partner <-emmeans(m_error1_votINV@model, pairwise ~ partner_type, adjust = "none", pbkrtest.limit = 3201)
# m_error_vot_1.emm_none_partner <- as.data.frame(m_error1_vot.emm_none_partner$contrasts)
# write.csv(m_error1_vot.emm_none_partner,"output_stats/LEALCO-BEH_error1_vot_ph_none_partner.csv", row.names = FALSE)
# 
# # extract and save marginal means
# m_error1_vot.mm_partner <- as.data.frame(m_error1_vot.emm_none_partner$emmeans)
# m_error1_vot.mm_partner$emmean_untrans <- 1/m_error1_vot.mm_partner$emmean
# m_error1_vot.mm_partner$lower.CL_untrans <- 1/m_error1_vot.mm_partner$upper.CL
# m_error1_vot.mm_partner$upper.CL_untrans <- 1/m_error1_vot.mm_partner$lower.CL
# write.csv(m_error1_vot.mm_partner,"output_stats/LEALCO-BEH_error1_vot_lmm_marginal_partner.csv", row.names = FALSE)
```

#### Error 2 - semantically related errors

```{r}

# # LMM
# error2_votINV <- error_votINV %>%
#   filter (error == 2)
# m_error2_votINV <- buildmer(f,data=error2_votINV,buildmerControl=buildmerControl(direction='order',
#           args=list(control=lmerControl(optimizer='bobyqa'))))
# summary(m_error1_votINV)
# 
# # save
# sink("output_stats/LEALCO-BEH_error2_vot_lmm.txt")
# print(summary(m_error2_votINV))
# sink()  # returns output to the console
```

```{r}
# # make post-hoc with no correction
# m_error2_vot.emm_none_partner <-emmeans(m_error1_votINV@model, pairwise ~ partner_type, adjust = "none", pbkrtest.limit = 3201)
# m_error_vot_2.emm_none_partner <- as.data.frame(m_error2_vot.emm_none_partner$contrasts)
# write.csv(m_error2_vot.emm_none_partner,"output_stats/LEALCO-BEH_error2_vot_ph_none_partner.csv", row.names = FALSE)
# 
# # extract and save marginal means
# m_error2_vot.mm_partner <- as.data.frame(m_error2_vot.emm_none_partner$emmeans)
# m_error2_vot.mm_partner$emmean_untrans <- 1/m_error2_vot.mm_partner$emmean
# m_error2_vot.mm_partner$lower.CL_untrans <- 1/m_error2_vot.mm_partner$upper.CL
# m_error2_vot.mm_partner$upper.CL_untrans <- 1/m_error2_vot.mm_partner$lower.UCL
# write.csv(m_error1_vot.mm_partner,"output_stats/LEALCO-BEH_error2_vot_lmm_marginal_partner.csv", row.names = FALSE)
```

```{r}
# # make post-hoc with no correction
# m_error2_vot.emm_none_partner <-emmeans(m_error2_votINV@model, pairwise ~ partner_type, adjust = "none", pbkrtest.limit = 3201)
# m_error_vot_2.emm_none_partner <- as.data.frame(m_error2_vot.emm_none_partner$contrasts)
# write.csv(m_error2_vot.emm_none_partner,"output_stats/LEALCO-BEH_error2_vot_ph_none_partner.csv", row.names = FALSE)
# 
# # extract and save marginal means
# m_error2_vot.mm_partner <- as.data.frame(m_error2_vot.emm_none_partner$emmeans)
# m_error2_vot.mm_partner$emmean_untrans <- 1/m_error2_vot.mm_partner$emmean
# m_error2_vot.mm_partner$lower.CL_untrans <- 1/m_error2_vot.mm_partner$upper.CL
# m_error2_vot.mm_partner$upper.CL_untrans <- 1/m_error2_vot.mm_partner$lower.CL
# write.csv(m_error2_vot.mm_partner,"output_stats/LEALCO-BEH_error2_vot_lmm_marginal_partner.csv", row.names = FALSE)
```

#### Error 4 - unrelated erros

```{r}
# 
# # LMM
# error4_votINV <- error_votINV %>%
#   filter (error == 4)
# m_error4_votINV <- buildmer(f,data=error4_votINV,buildmerControl=buildmerControl(direction='order',
#           args=list(control=lmerControl(optimizer='bobyqa'))))
# summary(m_error4_votINV)
# 
# # save
# sink("output_stats/LEALCO-BEH_error4_vot_lmm.txt")
# print(summary(m_error4_votINV))
# sink()  # returns output to the console
```

```{r}
# # make post-hoc with no correction
# m_error4_vot.emm_none_partner <-emmeans(m_error4_votINV@model, pairwise ~ partner_type, adjust = "none", pbkrtest.limit = 3201)
# m_error_vot_4.emm_none_partner <- as.data.frame(m_error4_vot.emm_none_partner$contrasts)
# write.csv(m_error4_vot.emm_none_partner,"output_stats/LEALCO-BEH_error2_vot_ph_none_partner.csv", row.names = FALSE)
# 
# # extract and save marginal means
# m_error4_vot.mm_partner <- as.data.frame(m_error4_vot.emm_none_partner$emmeans)
# m_error4_vot.mm_partner$emmean_untrans <- 1/m_error4_vot.mm_partner$emmean
# m_error4_vot.mm_partner$lower.CL_untrans <- 1/m_error4_vot.mm_partner$upper.CL
# m_error4_vot.mm_partner$upper.CL_untrans <- 1/m_error4_vot.mm_partner$lower.CL
# write.csv(m_error4_vot.mm_partner,"output_stats/LEALCO-BEH_error4_vot_lmm_marginal_partner.csv", row.names = FALSE)
```

#### Error all - Final figure

```{r}
# # plot
# pdf("output_figures/LEALCO-BEH_error_vot_lmm_marginal_partner.pdf",  width=10, height=3)
# p1 <- ggplot(m_error1_vot.mm_partner, aes(y=emmean_untrans, x=partner_type, color=partner_type)) + 
#   scale_colour_manual(values = pal1) +
#   geom_point(stat="identity", position=position_dodge(.9), size=3) +
#   geom_errorbar(aes(ymin=lower.CL_untrans, ymax=upper.CL_untrans), width=.2, position=position_dodge(.9)) +
#   labs(y="Naming Latencies\nfor compounded novel labels\n(proportion)", x="Partner Type") +
#   theme(axis.text=element_text(size=10), axis.title=element_text(size=12)) +
#   ylim(0,4000) 
# 
# p2 <- ggplot(m_error2_vot.mm_partner, aes(y=emmean_untrans, x=partner_type, color=partner_type)) + 
#   scale_colour_manual(values = pal1) +
#   geom_point(stat="identity", position=position_dodge(.9), size=3) +
#   geom_errorbar(aes(ymin=lower.CL_untrans, ymax=upper.CL_untrans), width=.2, position=position_dodge(.9)) +
#   labs(y="Naming Latencies\nfor semantically related novel labels (ms)", x="Partner Type") +
#   theme(axis.text=element_text(size=10), axis.title=element_text(size=12)) +
#   ylim(0,4000)
# 
# p4 <- ggplot(m_error4_vot.mm_partner, aes(y=emmean_untrans, x=partner_type, color=partner_type)) + 
#   scale_colour_manual(values = pal1) +
#   geom_point(stat="identity", position=position_dodge(.9), size=3) +
#   geom_errorbar(aes(ymin=lower.CL_untrans, ymax=upper.CL_untrans), width=.2, position=position_dodge(.9)) +
#   labs(y="Naming Latencies\nfor unrelated novel labels (ms)", x="Partner Type") +
#   theme(axis.text=element_text(size=10), axis.title=element_text(size=12)) +
#   ylim(0,4000)
# 
# grid.arrange(p1, p2, p4,ncol=3)
# 
# dev.off()  
```

# === 1-label items ===

```{r}
data_1label <- data %>%
  filter(type == '1-label') %>%
  filter(error %in% c('correct', '1t', '1a', '2t', '2a', '3t', '3a', '4'))
```

### Label Maintenance

```{r}
# aggregate within subject
label1_acc_wSubj <- data_1label %>%
  filter(!subjID %in% exclusion_acc) %>%
  group_by(subjID) %>%
  summarise(mean = mean(is_correct), sem=(sd(is_correct)/sqrt((length(is_correct)))), sd=sd(is_correct))

# aggregate between subjects
label1_acc_bSubj <- label1_acc_wSubj %>%
  summarise(grandMean = mean(mean), sem=(sd(mean)/sqrt((length(mean)))), sd=sd(mean))

# aggregate within subject
label1_acc_wSubj_partner <- data_1label %>%
  group_by(subjID, test_partner) %>%
  summarise(mean = mean(is_correct), sem=(sd(is_correct)/sqrt((length(is_correct)))), sd=sd(is_correct))

# aggregate between subjects
label1_acc_bSubj_partner <- label1_acc_wSubj_partner %>%
  group_by(test_partner) %>%
  summarise(grandMean = mean(mean), sem=(sd(mean)/sqrt((length(mean)))), sd=sd(mean))
```

#### LMM

```{r}
# select data
label1_acc <- data_1label %>%
  filter(!subjID %in%  exclusion_acc)

# Set sum contrasts for all variables.
contrasts(label1_acc$test_partner) <- contr.sum(2)
contrasts(label1_acc$block)  <- contr.sum(2)
contrasts(label1_acc$primacy)  <- contr.sum(2)
contrasts(label1_acc$training_order)  <- contr.sum(2)


# check contrasts
contrasts(label1_acc$test_partner)
contrasts(label1_acc$block)
contrasts(label1_acc$primacy)
contrasts(label1_acc$recency)
contrasts(label1_acc$training_order) 

# center continious covariates
label1_acc <- label1_acc %>%
  mutate(c_norm = norm - mean(norm, na.rm=TRUE))
```

```{r}
# indicate the maximal effect srucutre (both fixend and random) that is motivated based on design & hypotheses
f <- is_correct ~ test_partner*block * training_order +
     (test_partner * block * training_order | subjID) +
     (test_partner * block * training_order  | target_label)

# select the maximal model that still converges
label1_m_acc <- buildmer(f,family=binomial, data=label1_acc,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(label1_m_acc)

sink("output_stats/LEALCO-BEH2_label1_acc_lmm.txt")
print(summary(label1_m_acc))
sink()  # returns output to the console
```

#### Post - hoc

```{r}
# make post-hoc with no correction
label1_m_acc.emm_none_partner <-emmeans(label1_m_acc@model, pairwise ~ test_partner, adjust = "none")
label1_m_acc.ph_none_partner <- as.data.frame(label1_m_acc.emm_none_partner$contrasts)
write.csv(label1_m_acc.emm_none_partner,"output_stats/LEALCO-BEH2_label1_acc_ph_none_testpartner.csv", row.names = FALSE)

# extract and save marginal means
label1_m_acc.mm_partner <- as.data.frame(label1_m_acc.emm_none_partner$emmeans)
label1_m_acc.mm_partner$emmean_untrans <- plogis(label1_m_acc.mm_partner$emmean)
label1_m_acc.mm_partner$asymp.LCL_untrans <- plogis(label1_m_acc.mm_partner$asymp.LCL)
label1_m_acc.mm_partner$asymp.UCL_untrans <- plogis(label1_m_acc.mm_partner$asymp.UCL)

# save them
write.csv(label1_m_acc.mm_partner,"output_stats/LEALCO-BEH2_label1_acc_lmm_marginalMeans_partner.csv", row.names = FALSE)

# visualize marginal means
pdf("output_figures/LEALCO-BEH2_label1_acc_lmm_marginal_partner_pointplot.pdf")
tt <- ggplot(label1_m_acc.mm_partner, aes(y=emmean_untrans, x=test_partner, group=test_partner      )) +
  #scale_colour_manual(values = pal3) +
  geom_point(stat="identity", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=asymp.LCL_untrans, ymax=asymp.UCL_untrans), width=.2, position=position_dodge(.9)) +
  labs(y="Precedent maintenance\n(proportion)", x="Partner") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,1) 
tt
dev.off()
tt
```

### Naming Latency

```{r}
# aggregate within subject
label1_vot_wSubj <- data_1label %>%
  group_by(subjID) %>%
  filter(subjID %in% exclusion_vot) %>%
  filter(error == 'correct') %>%
  summarise(mean = mean(VOT), sem=(sd(VOT)/sqrt((length(VOT)))), sd=sd(VOT))

# aggregate between subjects
label1_vot_bSubj <- label1_vot_wSubj %>%
  summarise(grandMean = mean(mean), sem=(sd(mean)/sqrt((length(mean)))), sd=sd(mean))

# aggregate within subject
label1_vot_wSubj_partner <- data_1label %>%
  group_by(subjID, test_partner) %>%
  summarise(mean = mean(VOT), sem=(sd(VOT)/sqrt((length(VOT)))), sd=sd(VOT))

# aggregate between subjects
label1_vot_bSubj_partner <- label1_vot_wSubj_partner %>%
  group_by(test_partner) %>%
  summarise(grandMean = mean(mean), sem=(sd(mean)/sqrt((length(mean)))), sd=sd(mean))
```

#### LMM

```{r}

# select data
label1_vot <- data_1label %>%
  filter(!subjID %in%  exclusion_vot) %>%
  filter (error == 'correct')

# Set sum contrasts for all variables.
contrasts(label1_vot$test_partner) <- contr.sum(2)
contrasts(label1_vot$block)  <- contr.sum(2)
contrasts(label1_vot$primacy)  <- contr.sum(2)
contrasts(label1_vot$training_order)  <- contr.sum(2)


# check contrasts
contrasts(label1_vot$test_partner)
contrasts(label1_vot$block)
contrasts(label1_vot$primacy)
contrasts(label1_vot$recency)
contrasts(label1_vot$training_order) 

# center continious covariates
label1_vot <- label1_vot %>%
  mutate(c_norm = norm - mean(norm, na.rm=TRUE))
```

```{r}
# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- VOTinv ~ test_partner * block * training_order * c_norm +
     (test_partner*block * training_order  | subjID) +
     (test_partner*block * training_order  | target_label)

# select the maximal model that still converges
label1_m_votINV <- buildmer(f,data=label1_vot,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(label1_m_votINV)

# save output
sink("output_stats/LEALCO-BEH2_label1_votINV_lmm.txt")
print(summary(label1_m_votINV))
sink()  # returns output to the console
```

#### Post-hoc / marginam means (Partner)

```{r}

# make post-hoc with no correction
label1_m_votINV.emm_none_partner <-emmeans(label1_m_votINV@model, pairwise ~ test_partner, adjust = "none")
label1_m_votINV.ph_none_partner <- as.data.frame(label1_m_votINV.emm_none_partner$contrasts)
write.csv(label1_m_votINV.ph_none_partner,"output_stats/LEALCO-BEH2_label1_votINV_ph_none_partner.csv", row.names = FALSE)


# extract and save marginal means
label1_m_votINV.mm_partner <- as.data.frame(label1_m_votINV.emm_none_partner$emmeans)
label1_m_votINV.mm_partner$emmean_untrans <- 1/label1_m_votINV.mm_partner$emmean
label1_m_votINV.mm_partner$lower.CL_untrans <- 1/label1_m_votINV.mm_partner$upper.CL
label1_m_votINV.mm_partner$upper.CL_untrans <- 1/label1_m_votINV.mm_partner$lower.CL
write.csv(label1_m_votINV.mm_partner,"output_stats/LEALCO-BEH2_label1_votINV_lmm_marginal_partner.csv", row.names = FALSE)


# plot
pdf("output_figures/LEALCO-BEH2_label1_votINV_lmm_marginal_partner_pointplot.pdf")
tt <- ggplot(label1_m_votINV.mm_partner, aes(y=emmean_untrans, x=test_partner, color=test_partner)) +
  #scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(.9), size=3, col='black') +
  geom_errorbar(aes(ymin=lower.CL_untrans, ymax=upper.CL_untrans), width=.2, position=position_dodge(.9), col='black') +
  labs(y="Naming latencies (ms)", x="Partner") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,2500)
tt
dev.off()
tt
```

#### Post-hoc / marginam means (Partner)

```{r}
# make post-hoc with no correction
label1_m_votINV.emm_none_block <-emmeans(label1_m_votINV@model, pairwise ~ block, adjust = "none")
label1_m_votINV.ph_none_block <- as.data.frame(label1_m_votINV.emm_none_block$contrasts)
write.csv(label1_m_votINV.ph_none_block,"output_stats/LEALCO-BEH2_label1_votINV_ph_none_block.csv", row.names = FALSE)


# extract and save marginal means
label1_m_votINV.mm_block <- as.data.frame(label1_m_votINV.emm_none_block$emmeans)
label1_m_votINV.mm_block$emmean_untrans <- 1/label1_m_votINV.mm_block$emmean
label1_m_votINV.mm_block$lower.CL_untrans <- 1/label1_m_votINV.mm_block$upper.CL
label1_m_votINV.mm_block$upper.CL_untrans <- 1/label1_m_votINV.mm_block$lower.CL
write.csv(label1_m_votINV.mm_block,"output_stats/LEALCO-BEH2_label1_votINV_lmm_marginal_block.csv", row.names = FALSE)


# plot
pdf("output_figures/LEALCO-BEH2_label1_votINV_lmm_marginal_block_pointplot.pdf")
tt <- ggplot(label1_m_votINV.mm_block, aes(y=emmean_untrans, x=block, color=block)) +
  #scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(.9), size=3, col='black') +
  geom_errorbar(aes(ymin=lower.CL_untrans, ymax=upper.CL_untrans), width=.2, position=position_dodge(.9), col='black') +
  labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,2500)
tt
dev.off()
tt
```

# === 0-label items (untrained items) ===

```{r}
data_0label <- data %>%
  filter(type == 'untrained') %>%
  filter(error %in% c('correct', '1t', '1a', '2t', '2a', '3t', '3a', '4'))
```

## Accuracy

```{r}
# aggregate within subject
label0_acc_wSubj <- data_0label %>%
  filter(!subjID %in% exclusion_acc) %>%
  group_by(subjID) %>%
  summarise(mean = mean(is_correct), sem=(sd(is_correct)/sqrt((length(is_correct)))), sd=sd(is_correct))

# aggregate between subjects
label0_acc_bSubj <- label0_acc_wSubj %>%
  summarise(grandMean = mean(mean), sem=(sd(mean)/sqrt((length(mean)))), sd=sd(mean))

# aggregate within subject
label0_acc_wSubj_partner <- data_0label %>%
  group_by(subjID, test_partner) %>%
  summarise(mean = mean(is_correct), sem=(sd(is_correct)/sqrt((length(is_correct)))), sd=sd(is_correct))

# aggregate between subjects
label0_acc_bSubj_partner <- label0_acc_wSubj_partner %>%
  group_by(test_partner) %>%
  summarise(grandMean = mean(mean), sem=(sd(mean)/sqrt((length(mean)))), sd=sd(mean))
```

#### LMM

```{r}
# select data
label0_acc <- data_0label %>%
  filter(!subjID %in%  exclusion_acc)

# Set sum contrasts for all variables.
contrasts(label0_acc$test_partner) <- contr.sum(2)
contrasts(label0_acc$block)  <- contr.sum(2)
contrasts(label0_acc$primacy)  <- contr.sum(2)
contrasts(label0_acc$training_order)  <- contr.sum(2)


# check contrasts
contrasts(label0_acc$test_partner)
contrasts(label0_acc$block)
contrasts(label0_acc$primacy)
contrasts(label0_acc$recency)
contrasts(label0_acc$training_order) 

# center continious covariates
label0_acc <- label0_acc %>%
  mutate(c_norm = norm - mean(norm, na.rm=TRUE))
```

Note that the c_norm variable must be dropped here because it has values only for the "correct" responses. Therefore it cannot be used a predictor for whether a response was correct or not.

```{r}
# indicate the maximal effect srucutre (both fixend and random) that is motivated based on design & hypotheses
f <- is_correct ~ test_partner*block * training_order +
     (test_partner * block * training_order | subjID) +
     (test_partner * block * training_order  | target_label)

# select the maximal model that still converges
label0_m_acc <- buildmer(f,family=binomial, data=label0_acc,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(label0_m_acc)

sink("output_stats/LEALCO-BEH2_label0_acc_lmm.txt")
print(summary(label0_m_acc))
sink()  # returns output to the console
```

#### Post-hoc / marginal means

```{r}
# make post-hoc with no correction
label0_m_acc.emm_none_partner <-emmeans(label0_m_acc@model, pairwise ~ test_partner, adjust = "none")
label0_m_acc.ph_none_partner <- as.data.frame(label0_m_acc.emm_none_partner$contrasts)
write.csv(label0_m_acc.emm_none_partner,"output_stats/LEALCO-BEH2_label0_acc_ph_none_testpartner.csv", row.names = FALSE)

# extract and save marginal means
label0_m_acc.mm_partner <- as.data.frame(label0_m_acc.emm_none_partner$emmeans)
label0_m_acc.mm_partner$emmean_untrans <- plogis(label0_m_acc.mm_partner$emmean)
label0_m_acc.mm_partner$asymp.LCL_untrans <- plogis(label0_m_acc.mm_partner$asymp.LCL)
label0_m_acc.mm_partner$asymp.UCL_untrans <- plogis(label0_m_acc.mm_partner$asymp.UCL)

# save them
write.csv(label0_m_acc.mm_partner,"output_stats/LEALCO-BEH2_label0_acc_lmm_marginalMeans_partner.csv", row.names = FALSE)

# visualize marginal means
pdf("output_figures/LEALCO-BEH2_label0_acc_lmm_marginal_partner_pointplot.pdf")
tt <- ggplot(label0_m_acc.mm_partner, aes(y=emmean_untrans, x=test_partner, group=test_partner      )) +
  #scale_colour_manual(values = pal3) +
  geom_point(stat="identity", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=asymp.LCL_untrans, ymax=asymp.UCL_untrans), width=.2, position=position_dodge(.9)) +
  labs(y="Target Labels \n(proportion)", x="Partner") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,1) 
tt
dev.off()
tt
```

## Naming latencies

### By Subjects (native, frequency x block)

```{r}
# aggregate within subject
label0_vot_wSubj <- data_0label %>%
  group_by(subjID) %>%
  filter(subjID %in% exclusion_vot) %>%
  filter(error == 'correct') %>%
  summarise(mean = mean(VOT), sem=(sd(VOT)/sqrt((length(VOT)))), sd=sd(VOT))

# aggregate between subjects
label0_vot_bSubj <- label0_vot_wSubj %>%
  summarise(grandMean = mean(mean), sem=(sd(mean)/sqrt((length(mean)))), sd=sd(mean))

# aggregate within subject
label0_vot_wSubj_partner <- data_0label %>%
  group_by(subjID, test_partner) %>%
  summarise(mean = mean(VOT), sem=(sd(VOT)/sqrt((length(VOT)))), sd=sd(VOT))

# aggregate between subjects
label0_vot_bSubj_partner <- label0_vot_wSubj_partner %>%
  group_by(test_partner) %>%
  summarise(grandMean = mean(mean), sem=(sd(mean)/sqrt((length(mean)))), sd=sd(mean))
```

### LMM

```{r}
# select data
label0_vot <- data_0label %>%
  filter(!subjID %in%  exclusion_vot) %>%
  filter (error == 'correct')

# Set sum contrasts for all variables.
contrasts(label0_vot$test_partner) <- contr.sum(2)
contrasts(label0_vot$block)  <- contr.sum(2)
contrasts(label0_vot$primacy)  <- contr.sum(2)
contrasts(label0_vot$training_order)  <- contr.sum(2)


# check contrasts
contrasts(label0_vot$test_partner)
contrasts(label0_vot$block)
contrasts(label0_vot$primacy)
contrasts(label0_vot$recency)
contrasts(label0_vot$training_order) 

# center continious covariates
label0_vot <- label0_vot %>%
  mutate(c_norm = norm - mean(norm, na.rm=TRUE))
```

```{r}
# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- VOTinv ~ test_partner * block * training_order  +
     (test_partner*block * training_order  | subjID) +
     (test_partner*block * training_order  | target_label)

# select the maximal model that still converges
label0_m_votINV <- buildmer(f,data=label0_vot,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(label0_m_votINV)

# save output
sink("output_stats/LEALCO-BEH2_label0_votINV_lmm.txt")
print(summary(label0_m_votINV))
sink()  # returns output to the console
```

### Post-hoc / marginal means (Block)

```{r}
# make post-hoc with no correction
label0_m_votINV.emm_none_block <-emmeans(label0_m_votINV@model, pairwise ~ block, adjust = "none")
label0_m_votINV.ph_none_block <- as.data.frame(label0_m_votINV.emm_none_block$contrasts)
write.csv(label0_m_votINV.ph_none_block,"output_stats/LEALCO-BEH2_label0_votINV_ph_none_block.csv", row.names = FALSE)


# extract and save marginal means
label0_m_votINV.mm_block <- as.data.frame(label0_m_votINV.emm_none_block$emmeans)
label0_m_votINV.mm_block$emmean_untrans <- 1/label0_m_votINV.mm_block$emmean
label0_m_votINV.mm_block$lower.CL_untrans <- 1/label0_m_votINV.mm_block$upper.CL
label0_m_votINV.mm_block$upper.CL_untrans <- 1/label0_m_votINV.mm_block$lower.CL
write.csv(label0_m_votINV.mm_block,"output_stats/LEALCO-BEH2_label0_votINV_lmm_marginal_block.csv", row.names = FALSE)


# plot
pdf("output_figures/LEALCO-BEH2_label0_votINV_lmm_marginal_block_pointplot.pdf")
tt <- ggplot(label0_m_votINV.mm_block, aes(y=emmean_untrans, x=block, color=test_partner)) +
  #scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(.9), size=3, col='black') +
  geom_errorbar(aes(ymin=lower.CL_untrans, ymax=upper.CL_untrans), width=.2, position=position_dodge(.9), col='black') +
  labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,2500)
tt
dev.off()
tt
```

### 

# Session Information

```{r}
sessionInfo()
```
